
\def \LessonDay {\makecell{Combinations}}

\def \LearningCompetenciesDay {}

\def \ObjectivesDay {
\item Collect the steps in finding the rule of a given Combinations; 
\item Calculate the next terms of a Combinations; and, 
\item Show interest and perseverance in solving problems.
}

\def \TeachersGuideDay {pp. 0--0}

\def \LMPagesDay {pp. 0--0}

\def \TextbookPagesDay {pp. 0--0}

\def \AdditionalMaterialsDay {}

\def \OtherResourcesDay {Flashcards}

\def \ReviewDay {\input{/storage/emulated/0/Documents/documents/latex/1920/Grade-10/1st/combinations/vs-combinations-input}}

\def \PurposeDay {The purpose of this lesson is to enable the students to solve real life problems involving combinations.}  

\def \ExamplesDay {Some examples of combinations are the following: 
\begin{enumerate}[label = \arabic*. ]
%1
\item 
%2
\item 
%3
\item 
\end{enumerate}   
}

\def \PracticeOneDay {\input{/storage/emulated/0/Documents/documents/latex/1920/Grade-10/1st/combinations/ps-combinations-input1}}

\def \PracticeTwoDay {\input{/storage/emulated/0/Documents/documents/latex/1920/Grade-10/1st/combinations/ps-combinations-input2}
}

\def \MasteryDay {\input{/storage/emulated/0/Documents/documents/latex/1920/Grade-10/1st/combinations/ps-combinations-input3}}

\def \ApplicationDay { Let the students answer the following questions: 
\begin{enumerate}[label = \arabic*. ]
%1
\item In what real life situations or problems can we observe some examples of combinations? 
%2
\item How can you apply your knowledge of combinations in solving these real life problems? 
%3
%\item 
\end{enumerate}   
}

\def \GeneralizationDay {Let the students answer the following questions: 
\begin{enumerate}[label = \arabic*. ]
%1
\item In your own words, what are combinations? 
%2
\item How do we solve problems involving combinations? 
%3
%\item 
\end{enumerate}   
}

\def \EvaluationDay {
\input{/storage/emulated/0/Documents/documents/latex/1920/Grade-10/1st/combinations/qz-combinations-input} 
}

\def \RemediationDay {}
