% cd /storage/emulated/0/Documents/documents/latex/1920/Grade-10/tests/quiz-bee; pdflatex quiz-bee-oral.tex && termux-open quiz-bee-oral.pdf

\input{../tests-preamble} 

\linespread{1}

\newcommand{\ExamName}{Quiz Bee Oral Competition}

\begin{document}

\begin{center}
\textbf{Questions for Grade 10 Quiz Bee Oral Competition}
\end{center} 

\textbf{Easy Round} 
%\begin{center}
%\vspace*{2ex}
%\scalebox{1}{
%
%\noindent\begin{minipage}{\textwidth}
{\begin{enumerate}[label = \arabic*. ]
%\begin{multicols}{2}
%1
\item Evaluate: $0!(1!+2!+3!)$. (Answer: 9)
%2
\item What is the number of permutation of zero objects selected from a set of 5 objects? (Answer: 1)
%3
\item What do we call an arc with a measure equal to one-half the circumference of a circle? (Answer: Semicircle)
%4
\item What is the next term in the Fibonacci sequence 1, 1, 2, 3, 5, 8, \ldots?     (Answer: 13)
%5
\item What are the zeros of the polynomial function $h(x) = (x-2) (x + 1) (x-3)$? (Answer: 2, -1, 3)
%6
\item Which theorem states that ``If the polynomial $P(x)$ is divided by $(x-c)$, then the remainder is $P(c)$"?  (Answer: Remainder Theorem)
%7
\item What is the leading coefficient of the polynomial function \mbox{$f(x) = 3-2x^2 + 4x^4 + 5x^6$}. (Answer: 5)
%8
\item What is the next term in the geometric sequence  3, 9, 27, \ldots? (Answer: 81)
%9
\item How many  possible rational zeros does the following polynomial  function have: $P(x) = 5x^4  - 7x^2 + 3$? (Answer: 4)
%10
\item What is the leading term of the polynomial function $P(x) = 11x^2 - 3x^{7} + 2x^8 - 3$? (Answer: $2x^8$)
%\end{multicols} 
\end{enumerate}}
%\end{minipage}}
%\end{center} 

\textbf{Average Round} 
\begin{enumerate}[label = \arabic*. ]
%\begin{multicols}{2}
%1
\item How many 4-digit numbers can be formed from the digits 0, 1, 2, 3, 4, and 5, if repetition of digits is not allowed? (Answer: 300)
%2
\item How many ways can Cinderella arrange the seven dwarfs in a round table? (Answer: 720) 
%3
\item In the canteen, a meal order consists of appetizer, a dish and a dessert. There are 3 appetizers, 5 dishes, and 2 desserts. Find the number of ways a customer can have an order.(Answer: 30)
%4
\item How many ways can 6 keys be arranged in a key ring? (Answer: 60)
%5 
\item What is the measure of an inscribed angle that intercepts a semicircle? (Answer: $90 \degree$)
%\end{multicols} 
\end{enumerate} 

\textbf{Difficult Round} 
\begin{enumerate}[label = \arabic*. ]
%\begin{multicols}{2}
%1
\item Given six non-collinear, coplanar points, how many triangles can be formed using these points? (Answer: 20)
%2
\item In  how  many  ways  can 5  persons  be  seated  around  a  circular  table  if two  of  them  insist  on  sitting  beside  each  other? (Answer: 12)
%3
\item What are the x-intercepts of the function \mbox{$f(x) = x^2 (x +3)(x -2)$}? (Answer: 0, -3 and 2)
%4
\item According to Descartes' rule of signs, how many positive zeros does  the polynomial function $f(x) = 4x^5-6x^3 + 2x^2-6x-9$ have? (Answer: 3 or 1)
%5 
\item What is the remainder of  $3x^{100} - 4$  divided by $(x + 1)$?  (Answer: -1)
%\end{multicols} 
\end{enumerate} 
\end{document}
