 

\def \LessonDayA {Harmonic Sequence}

\def \LearningCompetenciesDayA {}

\def \ObjectivesDayA {
\item Describe the similarities between harmonic sequences and arithmetic sequences; 
\item Calculate the next terms  of a given harmonic sequence; and, 
\item Project independence and interest in solving problems.
}

\def \PurposeDayA {The purpose of this lesson is to enable the students to solve real life problems involving harmonic sequence.}  

\def \ApplicationDayA { Let the students answer the following questions: 
\begin{enumerate}[label = \arabic*. ]
%1
\item In what real life situations or problems can we observe some examples of harmonic sequence? 
%2
\item How can you apply your knowledge of harmonic sequence in solving these real life problems? 

\end{enumerate}   
}

\def \GeneralizationDayA {Let the students answer the following questions: 
\begin{enumerate}[label = \arabic*. ]
%1
\item In your own words, what is a harmonic sequence? 
%2
\item How do we solve problems involving harmonic sequence? 

\end{enumerate}   
}

\def \TeachersGuideDayA {pp. 83--91}

\def \LMPagesDayA {pp. 50--54}

\def \TextbookPagesDayA {pp. 70--76}

\def \AdditionalMaterialsDayA {}

\def \OtherResourcesDayA {Flashcards}

\def \ReviewDayA {\input{/host-rootfs/storage/emulated/0/Documents/documents/latex/1920/Grade-10/1st/harmonic-sequence/vs-harmonic-sequence-input}}



\def \ExamplesDayA {}

\def \PracticeOneDayA {\input{/host-rootfs/storage/emulated/0/Documents/documents/latex/1920/Grade-10/1st/harmonic-sequence/ps-harmonic-sequence-input1}}

\def \PracticeTwoDayA {\input{/host-rootfs/storage/emulated/0/Documents/documents/latex/1920/Grade-10/1st/harmonic-sequence/ps-harmonic-sequence-input2}
}

\def \MasteryDayA {\input{/host-rootfs/storage/emulated/0/Documents/documents/latex/1920/Grade-10/1st/harmonic-sequence/ps-harmonic-sequence-input3}}



\def \EvaluationDayA {
\input{/host-rootfs/storage/emulated/0/Documents/documents/latex/1920/Grade-10/1st/harmonic-sequence/qz-harmonic-sequence-input} 
}

\def \RemediationDayA {}

\def \LessonDayB {Fibonacci Sequence}

\def \LearningCompetenciesDayB {}

\def \ObjectivesDayB {
\item Describe the steps in finding the next terms of a  fibonacci sequence; 
\item Solve the next terms of a  fibonacci sequence; and, 
\item Show willingness and interest in solving problems.
}

\def \PurposeDayB {The purpose of this lesson is to enable the students to solve real life problems involving fibonacci sequence.}  

\def \ApplicationDayB { Let the students answer the following questions: 
\begin{enumerate}[label = \arabic*. ]
%1
\item In what real life situations or problems can we observe some examples of fibonacci sequence? 
%2
\item How can you apply your knowledge of fibonacci sequence in solving these real life problems? 

\end{enumerate}   
}

\def \GeneralizationDayB {Let the students answer the following questions: 
\begin{enumerate}[label = \arabic*. ]
%1
\item In your own words, what is a fibonacci sequence? 
%2
\item How do we solve problems involving fibonacci sequence? 

\end{enumerate}   
}

\def \TeachersGuideDayB {pp. 83--91}

\def \LMPagesDayB {pp. 50--54}

\def \TextbookPagesDayB {pp. 70--76}

\def \AdditionalMaterialsDayB {}

\def \OtherResourcesDayB {Flashcards}

\def \ReviewDayB {\input{/host-rootfs/storage/emulated/0/Documents/documents/latex/1920/Grade-10/1st/fibonacci-sequence/vs-fibonacci-sequence-input}}



\def \ExamplesDayB {}

\def \PracticeOneDayB {\input{/host-rootfs/storage/emulated/0/Documents/documents/latex/1920/Grade-10/1st/fibonacci-sequence/ps-fibonacci-sequence-input1}}

\def \PracticeTwoDayB {\input{/host-rootfs/storage/emulated/0/Documents/documents/latex/1920/Grade-10/1st/fibonacci-sequence/ps-fibonacci-sequence-input2}
}

\def \MasteryDayB {\input{/host-rootfs/storage/emulated/0/Documents/documents/latex/1920/Grade-10/1st/fibonacci-sequence/ps-fibonacci-sequence-input3}}



\def \EvaluationDayB {
\input{/host-rootfs/storage/emulated/0/Documents/documents/latex/1920/Grade-10/1st/fibonacci-sequence/qz-fibonacci-sequence-input} 
}

\def \RemediationDayB {}

\def \LessonDayC {Polynomial Function}

\def \LearningCompetenciesDayC {}

\def \ObjectivesDayC {
\item Describe the steps in finding the next terms of a  polynomial function; 
\item Solve the next terms of a  polynomial function; and, 
\item Show willingness and perseverance in solving problems.
}

\def \PurposeDayC {The purpose of this lesson is to enable the students to solve real life problems involving polynomial function.}  

\def \ApplicationDayC { Let the students answer the following questions: 
\begin{enumerate}[label = \arabic*. ]
%1
\item In what real life situations or problems can we observe some examples of polynomial function? 
%2
\item How can you apply your knowledge of polynomial function in solving these real life problems? 

\end{enumerate}   
}

\def \GeneralizationDayC {Let the students answer the following questions: 
\begin{enumerate}[label = \arabic*. ]
%1
\item In your own words, what is a polynomial function? 
%2
\item How do we solve problems involving polynomial function? 

\end{enumerate}   
}

\def \TeachersGuideDayC {pp. 62--66}

\def \LMPagesDayC {pp. 52--55}

\def \TextbookPagesDayC {pp. 62--66}

\def \AdditionalMaterialsDayC {}

\def \OtherResourcesDayC {Flashcards}

\def \ReviewDayC {\input{/host-rootfs/storage/emulated/0/Documents/documents/latex/1920/Grade-10/1st/polynomial-function/vs-polynomial-function-input}}



\def \ExamplesDayC {}

\def \PracticeOneDayC {\input{/host-rootfs/storage/emulated/0/Documents/documents/latex/1920/Grade-10/1st/polynomial-function/ps-polynomial-function-input1}}

\def \PracticeTwoDayC {\input{/host-rootfs/storage/emulated/0/Documents/documents/latex/1920/Grade-10/1st/polynomial-function/ps-polynomial-function-input2}
}

\def \MasteryDayC {\input{/host-rootfs/storage/emulated/0/Documents/documents/latex/1920/Grade-10/1st/polynomial-function/ps-polynomial-function-input3}}



\def \EvaluationDayC {
\input{/host-rootfs/storage/emulated/0/Documents/documents/latex/1920/Grade-10/1st/polynomial-function/qz-polynomial-function-input} 
}

\def \RemediationDayC {}

\def \LessonDayD {Synthetic Division}

\def \LearningCompetenciesDayD {}

\def \ObjectivesDayD {
\item Describe the steps in finding the next terms of a  synthetic division; 
\item Generate the next terms of a  synthetic division; and, 
\item Show willingness and determination in solving problems.
}

\def \PurposeDayD {The purpose of this lesson is to enable the students to solve real life problems involving synthetic division.}  

\def \ApplicationDayD { Let the students answer the following questions: 
\begin{enumerate}[label = \arabic*. ]
%1
\item In what real life situations or problems can we observe some examples of synthetic division? 
%2
\item How can you apply your knowledge of synthetic division in solving these real life problems? 

\end{enumerate}   
}

\def \GeneralizationDayD {Let the students answer the following questions: 
\begin{enumerate}[label = \arabic*. ]
%1
\item In your own words, what is a synthetic division? 
%2
\item How do we solve problems involving synthetic division? 

\end{enumerate}   
}

\def \TeachersGuideDayD {pp. 67--73}

\def \LMPagesDayD {pp. 56--61}

\def \TextbookPagesDayD {pp. 67--73}

\def \AdditionalMaterialsDayD {}

\def \OtherResourcesDayD {Flashcards}

\def \ReviewDayD {\input{/host-rootfs/storage/emulated/0/Documents/documents/latex/1920/Grade-10/1st/synthetic-division/vs-synthetic-division-input}}



\def \ExamplesDayD {}

\def \PracticeOneDayD {\input{/host-rootfs/storage/emulated/0/Documents/documents/latex/1920/Grade-10/1st/synthetic-division/ps-synthetic-division-input1}}

\def \PracticeTwoDayD {\input{/host-rootfs/storage/emulated/0/Documents/documents/latex/1920/Grade-10/1st/synthetic-division/ps-synthetic-division-input2}
}

\def \MasteryDayD {\input{/host-rootfs/storage/emulated/0/Documents/documents/latex/1920/Grade-10/1st/synthetic-division/ps-synthetic-division-input3}}



\def \EvaluationDayD {
\input{/host-rootfs/storage/emulated/0/Documents/documents/latex/1920/Grade-10/1st/synthetic-division/qz-synthetic-division-input} 
}

\def \RemediationDayD {}

\def \LessonDayE {Remainder Theorem}

\def \LearningCompetenciesDayE {}

\def \ObjectivesDayE {
\item Describe the steps in finding the next terms of a  remainder theorem; 
\item Find the next terms of a  remainder theorem; and, 
\item Show willingness and self-reliance in solving problems.
}

\def \PurposeDayE {The purpose of this lesson is to enable the students to solve real life problems involving remainder theorem.}  

\def \ApplicationDayE { Let the students answer the following questions: 
\begin{enumerate}[label = \arabic*. ]
%1
\item In what real life situations or problems can we observe some examples of remainder theorem? 
%2
\item How can you apply your knowledge of remainder theorem in solving these real life problems? 

\end{enumerate}   
}

\def \GeneralizationDayE {Let the students answer the following questions: 
\begin{enumerate}[label = \arabic*. ]
%1
\item In your own words, what is a remainder theorem? 
%2
\item How do we solve problems involving remainder theorem? 

\end{enumerate}   
}

\def \TeachersGuideDayE {pp. 74--78}

\def \LMPagesDayE {pp. 62--65}

\def \TextbookPagesDayE {pp. 74--78}

\def \AdditionalMaterialsDayE {}

\def \OtherResourcesDayE {Flashcards}

\def \ReviewDayE {\input{/host-rootfs/storage/emulated/0/Documents/documents/latex/1920/Grade-10/1st/remainder-theorem/vs-remainder-theorem-input}}



\def \ExamplesDayE {}

\def \PracticeOneDayE {\input{/host-rootfs/storage/emulated/0/Documents/documents/latex/1920/Grade-10/1st/remainder-theorem/ps-remainder-theorem-input1}}

\def \PracticeTwoDayE {\input{/host-rootfs/storage/emulated/0/Documents/documents/latex/1920/Grade-10/1st/remainder-theorem/ps-remainder-theorem-input2}
}

\def \MasteryDayE {\input{/host-rootfs/storage/emulated/0/Documents/documents/latex/1920/Grade-10/1st/remainder-theorem/ps-remainder-theorem-input3}}



\def \EvaluationDayE {
\input{/host-rootfs/storage/emulated/0/Documents/documents/latex/1920/Grade-10/1st/remainder-theorem/qz-remainder-theorem-input} 
}

\def \RemediationDayE {}
