
\def \LessonDay {Inscribed Angles and Intercepted Arcs}

\def \LearningCompetenciesDay {}

\def \ObjectivesDay {
\item %cogverbstart
Execute
%cogverbend
the inscribed angles and intercepted arcs; 
\item %psyverbstart
Generate
%psyverbend
the inscribed angles and intercepted arcs to determine whether a binomial is a factor of a given polynomial; and, 
\item %affverbstart
Display
%affverbend
%valsstart
perseverance and willingness
%valsend
in solving problems.
}

\def \PurposeDay {The purpose of this lesson is to enable the students to solve real life problems involving the inscribed angles and intercepted arcs.}  

\def \ApplicationDay { Let the students answer the following questions: 
\begin{enumerate}[label = \arabic*. ]
%1
\item In what real life situations or problems can we observe some examples of inscribed angles and intercepted arcs? 
%2
\item How can you apply your knowledge of inscribed angles and intercepted arcs in solving these real life problems? 

\end{enumerate}   
}

\def \GeneralizationDay {Let the students answer the following questions: 
\begin{enumerate}[label = \arabic*. ]
%1
\item In your own words, what is the inscribed angles and intercepted arcs? 
%2
\item How do we solve problems involving inscribed angles and intercepted arcs? 

\end{enumerate}   
}

\def \TeachersGuideDay {pp. 125--130}

\def \LMPagesDay {pp. 114--119}

\def \TextbookPagesDay {pp. 121--127}

\def \AdditionalMaterialsDay {}

\def \OtherResourcesDay {Flashcards}

\def \ReviewDay {\input{/storage/emulated/0/Documents/documents/latex/1920/Grade-10/2nd/inscribed-angles-and-intercepted-arcs/vs-inscribed-angles-and-intercepted-arcs-input}}



\def \ExamplesDay {}

\def \PracticeOneDay {\input{/storage/emulated/0/Documents/documents/latex/1920/Grade-10/2nd/inscribed-angles-and-intercepted-arcs/ps-inscribed-angles-and-intercepted-arcs-input1}}

\def \PracticeTwoDay {\input{/storage/emulated/0/Documents/documents/latex/1920/Grade-10/2nd/inscribed-angles-and-intercepted-arcs/ps-inscribed-angles-and-intercepted-arcs-input2}
}

\def \MasteryDay {\input{/storage/emulated/0/Documents/documents/latex/1920/Grade-10/2nd/inscribed-angles-and-intercepted-arcs/ps-inscribed-angles-and-intercepted-arcs-input3}}



\def \EvaluationDay {
\input{/storage/emulated/0/Documents/documents/latex/1920/Grade-10/2nd/inscribed-angles-and-intercepted-arcs/qz-inscribed-angles-and-intercepted-arcs-input} 
}

\def \RemediationDay {}
