
\def \LessonDay {Dividing Rational Algebraic Expressions}

\def \LearningCompetenciesDay {}

\def \ObjectivesDay {
\item %cogverbstart
Execute 
%cogverbend
the steps in dividing rational algebraic expressions; 
\item %psyverbstart
Find 
%psyverbend
the product of rational algebraic expressions; and, 
\item %affverbstart
Show 
%affverbend
%valsstart
perseverance and interest 
%valsend
in solving problems.
}

\def \PurposeDay {The purpose of this lesson is to enable the students to solve real life problems by dividing rational algebraic expressions.}  

\def \ApplicationDay { Let the students answer the following questions: 
\begin{enumerate}[label = \arabic*. ]
%1
\item In what real life situations or problems can we observe some examples of dividing rational algebraic expressions? 
%2
\item How can you apply your knowledge of dividing rational algebraic expressions in solving these real life problems? 
\end{enumerate}   
}

\def \GeneralizationDay {Let the students answer the following questions: 
\begin{enumerate}[label = \arabic*. ]
%1
\item In your own words, how do we multiply rational algebraic expressions? 
%2
\item How do we solve problems involving algebraic expressions that require dividing rational algebraic expressions? 
\end{enumerate}   
}

\def \TeachersGuideDay {pp. 189--201}

\def \LMPagesDay {pp. 206--218}

\def \TextbookPagesDay {pp. 224--237}

\def \AdditionalMaterialsDay {}

\def \OtherResourcesDay {Flashcards}

\def \ReviewDay {\input{/storage/emulated/0/Documents/documents/latex/1920/Grade-8/1st/dividing-rational-algebraic-expressions/vs-dividing-rational-algebraic-expressions-input}}


\def \ExamplesDay {}

\def \PracticeOneDay {\input{/storage/emulated/0/Documents/documents/latex/1920/Grade-8/1st/dividing-rational-algebraic-expressions/ps-dividing-rational-algebraic-expressions-input1}}

\def \PracticeTwoDay {\input{/storage/emulated/0/Documents/documents/latex/1920/Grade-8/1st/dividing-rational-algebraic-expressions/ps-dividing-rational-algebraic-expressions-input2}
}

\def \MasteryDay {\input{/storage/emulated/0/Documents/documents/latex/1920/Grade-8/1st/dividing-rational-algebraic-expressions/ps-dividing-rational-algebraic-expressions-input3}}

\def \EvaluationDay {
\input{/storage/emulated/0/Documents/documents/latex/1920/Grade-8/1st/dividing-rational-algebraic-expressions/qz-dividing-rational-algebraic-expressions-input} 
}

\def \RemediationDay {}
