
\def \LessonDay {Solving Systems of Linear Equations by the Elimination Method}

\def \LearningCompetenciesDay {}

\def \ObjectivesDay {
\item %cogverbstart
Distinguish
%cogverbend
rational equations; 
\item %psyverbstart
Solve
%psyverbend
solutions to rational equations; and, 
\item %affverbstart
Demonstrate
%affverbend
%valsstart
determination and self-reliance
%valsend
in solving problems.
}

\def \PurposeDay {The purpose of this lesson is to enable the students to solve real life problems involving rational equations.}  

\def \ApplicationDay { Let the students answer the following questions: 
\begin{enumerate}[label = \arabic*. ]
%1
\item In what real life situations or problems can we observe some examples of rational equations? 
%2
\item How can you apply your knowledge of rational equations in solving these real life problems? 
\end{enumerate}   
}

\def \GeneralizationDay {Let the students answer the following questions: 
\begin{enumerate}[label = \arabic*. ]
%1
\item In your own words, what are rational equations? 
%2
\item How do we solve rational equations? 
\end{enumerate}   
}

\def \TeachersGuideDay {pp. 231--238}

\def \LMPagesDay {pp. 227--233}

\def \TextbookPagesDay {pp. 231--237}

\def \AdditionalMaterialsDay {}

\def \OtherResourcesDay {Flashcards}

\def \ReviewDay {\input{/storage/emulated/0/Documents/documents/latex/1920/Grade-8/2nd/solving-systems-of-linear-equations-by-the-elimination-method/vs-solving-systems-of-linear-equations-by-the-elimination-method-input}}


\def \ExamplesDay {}

\def \PracticeOneDay {\input{/storage/emulated/0/Documents/documents/latex/1920/Grade-8/2nd/solving-systems-of-linear-equations-by-the-elimination-method/ps-solving-systems-of-linear-equations-by-the-elimination-method-input1}}

\def \PracticeTwoDay {\input{/storage/emulated/0/Documents/documents/latex/1920/Grade-8/2nd/solving-systems-of-linear-equations-by-the-elimination-method/ps-solving-systems-of-linear-equations-by-the-elimination-method-input2}
}

\def \MasteryDay {\input{/storage/emulated/0/Documents/documents/latex/1920/Grade-8/2nd/solving-systems-of-linear-equations-by-the-elimination-method/ps-solving-systems-of-linear-equations-by-the-elimination-method-input3}}

\def \EvaluationDay {
\input{/storage/emulated/0/Documents/documents/latex/1920/Grade-8/2nd/solving-systems-of-linear-equations-by-the-elimination-method/qz-solving-systems-of-linear-equations-by-the-elimination-method-input} 
}

\def \RemediationDay {}
