
\def \LessonDay {Equation and Graph of a Circle}

\def \LearningCompetenciesDay {}

\def \ObjectivesDay {
\item %cogverbstart
Compare
%cogverbend
the equation and graph of a circle; 
\item %psyverbstart
Find
%psyverbend
the equation and graph of a circle to determine whether a binomial is a factor of a given polynomial; and, 
\item %affverbstart
Display
%affverbend
%valsstart
interest and perseverance
%valsend
in solving problems.
}

\def \PurposeDay {The purpose of this lesson is to enable the students to solve real life problems involving the equation and graph of a circle.}  

\def \ApplicationDay { Let the students answer the following questions: 
\begin{enumerate}[label = \arabic*. ]
%1
\item In what real life situations or problems can we observe some examples of equation and graph of a circle? 
%2
\item How can you apply your knowledge of equation and graph of a circle in solving these real life problems? 

\end{enumerate}   
}

\def \GeneralizationDay {Let the students answer the following questions: 
\begin{enumerate}[label = \arabic*. ]
%1
\item In your own words, what is the equation and graph of a circle? 
%2
\item How do we solve problems involving equation and graph of a circle? 

\end{enumerate}   
}

\def \TeachersGuideDay {pp. 155--160}

\def \LMPagesDay {pp. 144--149}

\def \TextbookPagesDay {pp. 157--163}

\def \AdditionalMaterialsDay {}

\def \OtherResourcesDay {Flashcards}

\def \ReviewDay {\input{/storage/emulated/0/Documents/documents/latex/1920/Grade-10/3rd/equation-and-graph-of-a-circle/vs-equation-and-graph-of-a-circle-input}}



\def \ExamplesDay {}

\def \PracticeOneDay {\input{/storage/emulated/0/Documents/documents/latex/1920/Grade-10/3rd/equation-and-graph-of-a-circle/ps-equation-and-graph-of-a-circle-input1}}

\def \PracticeTwoDay {\input{/storage/emulated/0/Documents/documents/latex/1920/Grade-10/3rd/equation-and-graph-of-a-circle/ps-equation-and-graph-of-a-circle-input2}
}

\def \MasteryDay {\input{/storage/emulated/0/Documents/documents/latex/1920/Grade-10/3rd/equation-and-graph-of-a-circle/ps-equation-and-graph-of-a-circle-input3}}



\def \EvaluationDay {
\input{/storage/emulated/0/Documents/documents/latex/1920/Grade-10/3rd/equation-and-graph-of-a-circle/qz-equation-and-graph-of-a-circle-input} 
}

\def \RemediationDay {}
