
\def \LessonDay {\makecell{Product of a Sum and a Difference}}

\def \LearningCompetenciesDay {}

\def \ObjectivesDay {
\item Derive the formula  in finding the product of a sum and a difference; 
\item Find the product of a sum and a difference; and, 
\item Project determination and willingness in solving problems.
}

\def \PurposeDay {The purpose of this lesson is to enable the students to solve real life problems involving the product of a sum and a difference.}  

\def \ApplicationDay { Let the students answer the following questions: 
\begin{enumerate}[label = \arabic*. ]
%1
\item In what real life situations or problems can we observe some examples of the product of a sum and a difference? 
%2
\item How can you apply your knowledge of product of a sum and a difference in solving these real life problems? 
%3
%\item 
\end{enumerate}   
}

\def \GeneralizationDay {Let the students answer the following questions: 
\begin{enumerate}[label = \arabic*. ]
%1
\item In your own words, how do we get the product of a sum and a difference? 
%2
\item How do we solve problems involving the product of a sum and a difference? 
%3
%\item 
\end{enumerate}   
}


\def \TeachersGuideDay {pp. 16--21}

\def \LMPagesDay {pp. 14--18}

\def \TextbookPagesDay {pp. 18--23}

\def \AdditionalMaterialsDay {}

\def \OtherResourcesDay {Flashcards}

\def \ReviewDay {\input{/storage/emulated/0/Documents/documents/latex/1920/Grade-8/1st/product-of-a-sum-and-a-difference/vs-product-of-a-sum-and-a-difference-input}}


\def \ExamplesDay {Some examples of product-of-a-sum-and-a-difference are the following: 
\begin{enumerate}[label = \arabic*. ]
\item \hspce $(x - y)^{2} = x^{2} - 2xy + y^2$
%2
\item \hspce $(m + 2n^2)^{2} = m^2 + 4mn^2 + 4n^4 $
%3
\item \hspce $(-2a^3 - 3b^2)^{2} = 4a^6 + 12a^3b^2 + 9b^4 $
\end{enumerate}   
}

\def \PracticeOneDay {\input{/storage/emulated/0/Documents/documents/latex/1920/Grade-8/1st/product-of-a-sum-and-a-difference/ps-product-of-a-sum-and-a-difference-input1}}

\def \PracticeTwoDay {\input{/storage/emulated/0/Documents/documents/latex/1920/Grade-8/1st/product-of-a-sum-and-a-difference/ps-product-of-a-sum-and-a-difference-input2}
}

\def \MasteryDay {\input{/storage/emulated/0/Documents/documents/latex/1920/Grade-8/1st/product-of-a-sum-and-a-difference/ps-product-of-a-sum-and-a-difference-input3}}


\def \EvaluationDay {
\input{/storage/emulated/0/Documents/documents/latex/1920/Grade-8/1st/product-of-a-sum-and-a-difference/qz-product-of-a-sum-and-a-difference-input} 
}

\def \RemediationDay {}
