
\def \LessonDay {Circles and Related Terms}

\def \LearningCompetenciesDay {}

\def \ObjectivesDay {
\item %cogverbstart
Evaluate
%cogverbend
the circles and related terms; 
\item %psyverbstart
Compute
%psyverbend
the circles and related terms to determine whether a binomial is a factor of a given polynomial; and, 
\item %affverbstart
Display
%affverbend
%valsstart
self-reliance and willingness
%valsend
in solving problems.
}

\def \PurposeDay {The purpose of this lesson is to enable the students to solve real life problems involving the circles and related terms.}  

\def \ApplicationDay { Let the students answer the following questions: 
\begin{enumerate}[label = \arabic*. ]
%1
\item In what real life situations or problems can we observe some examples of circles and related terms? 
%2
\item How can you apply your knowledge of circles and related terms in solving these real life problems? 

\end{enumerate}   
}

\def \GeneralizationDay {Let the students answer the following questions: 
\begin{enumerate}[label = \arabic*. ]
%1
\item In your own words, what is the circles and related terms? 
%2
\item How do we solve problems involving circles and related terms? 

\end{enumerate}   
}

\def \TeachersGuideDay {pp. 121--124}

\def \LMPagesDay {pp. 110--113}

\def \TextbookPagesDay {pp. 116--120}

\def \AdditionalMaterialsDay {}

\def \OtherResourcesDay {Flashcards}

\def \ReviewDay {\input{/storage/emulated/0/Documents/documents/latex/1920/Grade-10/1st/circles-and-related-terms/vs-circles-and-related-terms-input}}



\def \ExamplesDay {}

\def \PracticeOneDay {\input{/storage/emulated/0/Documents/documents/latex/1920/Grade-10/1st/circles-and-related-terms/ps-circles-and-related-terms-input1}}

\def \PracticeTwoDay {\input{/storage/emulated/0/Documents/documents/latex/1920/Grade-10/1st/circles-and-related-terms/ps-circles-and-related-terms-input2}
}

\def \MasteryDay {\input{/storage/emulated/0/Documents/documents/latex/1920/Grade-10/1st/circles-and-related-terms/ps-circles-and-related-terms-input3}}



\def \EvaluationDay {
\input{/storage/emulated/0/Documents/documents/latex/1920/Grade-10/1st/circles-and-related-terms/qz-circles-and-related-terms-input} 
}

\def \RemediationDay {}
