\textbf{Practice Exercises}
%\textbf{Problem Set}

\vspce

Solve each problem completely.
\begin{enumerate}[label = \arabic*. ]
%\begin{multicols}{2}
%1
\item In a school, the probability that a student takes environmental science 
and geography is 0.25. The probability that a student takes environmental 
science is 0.72. What is probability that a student takes geography given 
that the student is taking environmental science?
%2
\item In certain population, the probability that a men lives to at least seventy-five years long is 0.75. The probability that he will live to at least eighty-five 
years is 0.65. If a man is seventy-five years old, what is the 
probability that  he will survive to eighty-five years?
%3
\item In a bag are economics and math books. Two books are chosen at 
random without replacement. The probability of selecting an economics book 
and then a math book is 0.42. The probability of selecting an economics 
book on the first draw is 0.62. What is probability of selecting a math book on 
the second draw given that the first book was economics? 
%4
\item In a box are a carton of dairy milk and Boonville chocolates. Two items 
are chosen at random from the box, without replacement. The probability of 
selecting dairy milk and then a Boonville chocolate is 0.47. The probability of 
selecting dairy milk on the first draw is 0.71. What is probability of selecting a 
Boonville chocolate on the second draw given that the first chocolate drawn was dairy milk? 
%5 
\item You roll two dice. The first die shows a TWO and the other die rolls under 
the table and you cannot see it. Now, what is the probability that both die 
show TWO?
%\end{multicols} 
\end{enumerate} 
