
\def \LessonDay {Probability of Dependent and Independent Events}

\def \LearningCompetenciesDay {}

\def \ObjectivesDay {
\item %cogverbstart
Distinguish
%cogverbend
the distinguishable-probability-of-dependent-and-independent-events; 
\item %psyverbstart
Compute
%psyverbend
the distinguishable-probability-of-dependent-and-independent-events to determine whether a binomial is a factor of a given polynomial; and, 
\item %affverbstart
Project
%affverbend
%valsstart
enjoyment and perseverance
%valsend
in solving problems.
}

\def \PurposeDay {The purpose of this lesson is to enable the students to solve real life problems involving the distinguishable-probability-of-dependent-and-independent-events.}  

\def \ApplicationDay { Let the students answer the following questions: 
\begin{enumerate}[label = \arabic*. ]
%1
\item In what real life situations or problems can we observe some examples of distinguishable-probability-of-dependent-and-independent-events? 
%2
\item How can you apply your knowledge of distinguishable-probability-of-dependent-and-independent-events in solving these real life problems? 

\end{enumerate}   
}

\def \GeneralizationDay {Let the students answer the following questions: 
\begin{enumerate}[label = \arabic*. ]
%1
\item In your own words, what is the distinguishable-probability-of-dependent-and-independent-events? 
%2
\item How do we solve problems involving distinguishable-probability-of-dependent-and-independent-events? 

\end{enumerate}   
}

\def \TeachersGuideDay {pp. 347--352}

\def \LMPagesDay {pp. 332--337}

\def \TextbookPagesDay {pp. 360--365}

\def \AdditionalMaterialsDay {}

\def \OtherResourcesDay {Flashcards}

\def \ReviewDay {\input{/storage/emulated/0/Documents/documents/latex/1920/Grade-10/3rd/distinguishable-probability-of-dependent-and-independent-events/vs-distinguishable-probability-of-dependent-and-independent-events-input}}



\def \ExamplesDay {}

\def \PracticeOneDay {\input{/storage/emulated/0/Documents/documents/latex/1920/Grade-10/3rd/distinguishable-probability-of-dependent-and-independent-events/ps-distinguishable-probability-of-dependent-and-independent-events-input1}}

\def \PracticeTwoDay {\input{/storage/emulated/0/Documents/documents/latex/1920/Grade-10/3rd/distinguishable-probability-of-dependent-and-independent-events/ps-distinguishable-probability-of-dependent-and-independent-events-input2}
}

\def \MasteryDay {\input{/storage/emulated/0/Documents/documents/latex/1920/Grade-10/3rd/distinguishable-probability-of-dependent-and-independent-events/ps-distinguishable-probability-of-dependent-and-independent-events-input3}}



\def \EvaluationDay {
%\input{/storage/emulated/0/Documents/documents/latex/1920/Grade-10/3rd/distinguishable-probability-of-dependent-and-independent-events/qz-distinguishable-probability-of-dependent-and-independent-events-input} 
}

\def \RemediationDay {}
