%\textbf{Practice Exercises}
\textbf{Problem Set}

\vspce

A. State whether the events are independent or dependent.

\begin{enumerate}[label = \arabic*. ]
%1
\item Deni has a blue, red, and green  tie. He  also has a blue  and green shirt.  Deni chooses a random  tie and shirt for work today. 

%2
\item Amboy plays card games. He  picks a card at  random. Then without putting the first card back, he picks a second card at random. 

%3
\item Canady  has 10 handmade sheets. She takes 6 sheets at random. Then  without putting these sheets  back, she picks 2 sheets at random.

\item Jeff has 3 children. His first 2 children are boys. His last child is a girl.

\item A tree has 4 red flowers and 2 blue flowers. Brandy  plucks 1 flower from the tree. After some time her sister plucks a flower from the same tree.


\end{enumerate}  

B. Solve each problem completely. 
\begin{enumerate}[label = \arabic*. ]
%1
%\item A box contains 4 red socks, 3 white socks, and 3 blue socks. Without looking, you select a sock at random, replace it, and select a second sock at random. What is the probability that the first sock is blue and the second sock is red?  
%2
\item A box of chocolates contains 10 milk chocolates, 8 dark chocolates, and 6 white chocolates. Hanissa randomly chooses a chocolate, eats 
it, and then randomly chooses another chocolate. What is the 
probability that Hanissa chose a milk chocolate, and then, a white chocolate? 

%3
%\item A rental agency has 12 white cars, 8 gray cars, 6 red cars, and 3 green cars for rent. Mang Canor rents a car, returns it because the radio is broken, and gets another car. What is the probability that Mr. Escobar is given a green car and then a gray car? 
%4
\item A toy box contains 12 toys, 8 stuffed animals, and 3 board games. Maria randomly chooses 2 toys for the child she is babysitting to play 
with. What is the probability that she chose 2 stuffed animals as the first two choices? 

%5
%\item A basket contains 6 apples, 5 bananas, 4 oranges, and 5 guavas. Dominic randomly chooses one piece of fruit, eats it, and chooses another piece of fruit. What is the probability that he chose a banana and then an apple?

%6
\item Nick has 4 black pens, 3 blue pens, and 2 red pens in his school bag. He randomly picks two pens out of his school bag. What is the probability that Nick chose two blue pens if he replaced the first pen back in his bag before choosing a second pen? 
%7
\item A bag contains 6 black marbles, 9 blue marbles, 4 yellow marbles, and 2 green marbles. A marble is randomly selected, replaced, and a second marble is randomly selected. Find the probability of selecting a black marble, then a yellow marble. 
%8
%\item A box contains 7 white marbles and 7 red marbles. What is the probability of drawing 2 white marbles and 1 red marble in succession without replacement? 
%9
%\item 
%10
%\item 
\end{enumerate}   
