\textbf{Practice Exercises}
%\textbf{Problem Set}

\vspce

A. State whether the events are independent or dependent.

\begin{enumerate}[label = \arabic*. ]
%1
\item Selecting a math book and a science book in a shelf.
%2
\item Chips are numbered 1 through 15 and placed in a box. Three of them are selected one after the other without replacing any of the chip.
%3
\item Answering the questions of a 5-item true-false test.

\item Juan has 14 coins. He takes 3 of them  at  random, then he puts  these back, and then picks 2 more coins at  random.

\item Getting a face card in the first draw from a deck of playing cards and getting a face card in the second draw. (The first card is not replaced.)

\end{enumerate}  

B. Solve each problem completely. 
\begin{enumerate}[label = \arabic*. ]
%1
\item A box contains 4 red socks, 3 white socks, and 3 blue socks. Without looking, you select a sock at random, replace it, and select a second sock at random. What is the probability that the first sock is blue and the second sock is red?  
%2
\item A rental agency has 12 white cars, 8 gray cars, 6 red cars, and 3 green cars for rent. Mang Canor rents a car, returns it because the radio is broken, and gets another car. What is the probability that Mang Canor is given a green car and then a gray car? 
%4
%\item A box of chocolates contains 10 milk chocolates, 8 dark chocolates, and 6 white chocolates. Hanissa randomly chooses a chocolate, eats it, and then randomly chooses another chocolate. What is the probability that Hanissa chose a milk chocolate, and then, a white chocolate? 

%3

%\item 
%10
%\item 
\end{enumerate}   
