
\def \LessonDay {\makecell{Sequences}}

\def \LearningCompetenciesDay {}

\def \ObjectivesDay {
\item Evaluate the rules of given sequences; 
\item Calculate the next terms of a given sequences; and, 
\item Exhibit interest and perseverance in solving problems.
}

\def \TeachersGuideDay {pp. 1--10}

\def \LMPagesDay {pp. 1--6}

\def \TextbookPagesDay {pp. 1--8}

\def \AdditionalMaterialsDay {}

\def \OtherResourcesDay {Flashcards}

\def \ReviewDay {\input{/storage/emulated/0/Documents/documents/latex/1920/Grade-10/1st/sequences/vs-sequences-input}}

\def \PurposeDay {The purpose of this lesson is to enable the students to solve real life problems involving sequences.}  

\def \ExamplesDay {Some examples of sequences are the following: 
\begin{enumerate}[label = \arabic*. ]
%1
\item \hspce  -2, 4, -8, 16,... 
\item \hspce  4, 1, -2, -5,... 
\item \hspce  1, 8, 27, 64,... 
\end{enumerate}   
}

\def \PracticeOneDay {\input{/storage/emulated/0/Documents/documents/latex/1920/Grade-10/1st/sequences/ps-sequences-input1}}

\def \PracticeTwoDay {\input{/storage/emulated/0/Documents/documents/latex/1920/Grade-10/1st/sequences/ps-sequences-input2}
}

\def \MasteryDay {\input{/storage/emulated/0/Documents/documents/latex/1920/Grade-10/1st/sequences/ps-sequences-input3}}

\def \ApplicationDay { Let the students answer the following questions: 
\begin{enumerate}[label = \arabic*. ]
%1
\item In what real life situations or problems can we observe some examples of sequences? 
%2
\item How can you apply your knowledge of sequences in solving these real life problems? 
%3
%\item 
\end{enumerate}   
}

\def \GeneralizationDay {Let the students answer the following questions: 
\begin{enumerate}[label = \arabic*. ]
%1
\item In your own words, what are sequences? 
%2
\item How do we solve problems involving sequences? 
%3
%\item 
\end{enumerate}   
}

\def \EvaluationDay {
\input{/storage/emulated/0/Documents/documents/latex/1920/Grade-10/1st/sequences/qz-sequences-input} 
}

\def \RemediationDay {}
