
\def \LessonDay {Finding Rational Zeros}

\def \LearningCompetenciesDay {}

\def \ObjectivesDay {
\item %cogverbstart
Classify
%cogverbend
the finding rational zeros; 
\item %psyverbstart
Calculate
%psyverbend
the finding rational zeros to determine whether a binomial is a factor of a given polynomial; and, 
\item %affverbstart
Display
%affverbend
%valsstart
determination and self-reliance
%valsend
in solving problems.
}

\def \PurposeDay {The purpose of this lesson is to enable the students to solve real life problems involving the finding rational zeros.}  

\def \ApplicationDay { Let the students answer the following questions: 
\begin{enumerate}[label = \arabic*. ]
%1
\item In what real life situations or problems can we observe some examples of finding rational zeros? 
%2
\item How can you apply your knowledge of finding rational zeros in solving these real life problems? 

\end{enumerate}   
}

\def \GeneralizationDay {Let the students answer the following questions: 
\begin{enumerate}[label = \arabic*. ]
%1
\item In your own words, what is the finding rational zeros? 
%2
\item How do we solve problems involving finding rational zeros? 

\end{enumerate}   
}

\def \TeachersGuideDay {pp. 86--90}

\def \LMPagesDay {pp. 72--75}

\def \TextbookPagesDay {pp. 86--90}

\def \AdditionalMaterialsDay {}

\def \OtherResourcesDay {Flashcards}

\def \ReviewDay {\input{/storage/emulated/0/Documents/documents/latex/1920/Grade-10/1st/finding-rational-zeros/vs-finding-rational-zeros-input}}



\def \ExamplesDay {}

\def \PracticeOneDay {\input{/storage/emulated/0/Documents/documents/latex/1920/Grade-10/1st/finding-rational-zeros/ps-finding-rational-zeros-input1}}

\def \PracticeTwoDay {\input{/storage/emulated/0/Documents/documents/latex/1920/Grade-10/1st/finding-rational-zeros/ps-finding-rational-zeros-input2}
}

\def \MasteryDay {\input{/storage/emulated/0/Documents/documents/latex/1920/Grade-10/1st/finding-rational-zeros/ps-finding-rational-zeros-input3}}



\def \EvaluationDay {
\input{/storage/emulated/0/Documents/documents/latex/1920/Grade-10/1st/finding-rational-zeros/qz-finding-rational-zeros-input} 
}

\def \RemediationDay {}
