
\def \LessonDay {Factoring Trinomials with 1 as Leading Coefficient}

\def \LearningCompetenciesDay {}

\def \ObjectivesDay {
\item Tell the steps in factoring trinomials with 1 as leading coefficient; 
\item Compute the factors of  trinomials with 1 as leading coefficient; and, 
\item Project enjoyment and enjoyment in solving problems.
}

\def \PurposeDay {The purpose of this lesson is to enable the students to solve real life problems by factoring trinomials with 1 as leading coefficient.}  

\def \ApplicationDay { Let the students answer the following questions: 
\begin{enumerate}[label = \arabic*. ]
%1
\item In what real life situations or problems can we observe some examples of factoring trinomials with 1 as leading coefficient? 
%2
\item How can you apply your knowledge of factoring trinomials with 1 as leading coefficient in solving these real life problems? 
\end{enumerate}   
}

\def \GeneralizationDay {Let the students answer the following questions: 
\begin{enumerate}[label = \arabic*. ]
%1
\item In your own words, how do we  factor trinomials with 1 as leading coefficient? 
%2
\item How do we solve problems involving algebraic expressions that require  factoring trinomials with 1 as leading coefficient? 
\end{enumerate}   
}

\def \TeachersGuideDay {pp. 58--63}

\def \LMPagesDay {pp. 50--54}

\def \TextbookPagesDay {pp. 67--73}

\def \AdditionalMaterialsDay {}

\def \OtherResourcesDay {Flashcards}

\def \ReviewDay {\input{/storage/emulated/0/Documents/documents/latex/1920/Grade-8/1st/factoring-trinomials-with-1-as-leading-coefficient/vs-factoring-trinomials-with-1-as-leading-coefficient-input}}


\def \ExamplesDay {}

\def \PracticeOneDay {\input{/storage/emulated/0/Documents/documents/latex/1920/Grade-8/1st/factoring-trinomials-with-1-as-leading-coefficient/ps-factoring-trinomials-with-1-as-leading-coefficient-input1}}

\def \PracticeTwoDay {\input{/storage/emulated/0/Documents/documents/latex/1920/Grade-8/1st/factoring-trinomials-with-1-as-leading-coefficient/ps-factoring-trinomials-with-1-as-leading-coefficient-input2}
}

\def \MasteryDay {\input{/storage/emulated/0/Documents/documents/latex/1920/Grade-8/1st/factoring-trinomials-with-1-as-leading-coefficient/ps-factoring-trinomials-with-1-as-leading-coefficient-input3}}

\def \EvaluationDay {
\input{/storage/emulated/0/Documents/documents/latex/1920/Grade-8/1st/factoring-trinomials-with-1-as-leading-coefficient/qz-factoring-trinomials-with-1-as-leading-coefficient-input} 
}

\def \RemediationDay {}
