
\def \LessonDay {\makecell{Arithmetic Means}}

\def \LearningCompetenciesDay {}

\def \ObjectivesDay {
\item State the steps in finding the arithmetic mean; 
\item Generate the arithmetic mean given  two terms of a sequence; and, 
\item Display interest and willingness in solving problems.
}

\def \TeachersGuideDay {pp. 22--30}

\def \LMPagesDay {pp. 14--18}

\def \TextbookPagesDay {pp. 19--25}

\def \AdditionalMaterialsDay {}

\def \OtherResourcesDay {Flashcards}

\def \ReviewDay {\input{/storage/emulated/0/Documents/documents/latex/1920/Grade-10/1st/arithmetic-means/vs-arithmetic-means-input}}

\def \PurposeDay {The purpose of this lesson is to enable the students to solve real life problems involving arithmetic means.}  

\def \ExamplesDay {Some examples of arithmetic means are the following: 
\begin{enumerate}[label = \arabic*. ]
%1
\item The arithmetic mean of 7 and 11 is 9.
%2
\item The arithmetic mean of 21 and 35 is 28.
%3
\item The two arithmetic means between 7 and 13 are 9 and 11.
\end{enumerate}   
}

\def \PracticeOneDay {\input{/storage/emulated/0/Documents/documents/latex/1920/Grade-10/1st/arithmetic-means/ps-arithmetic-means-input1}}

\def \PracticeTwoDay {\input{/storage/emulated/0/Documents/documents/latex/1920/Grade-10/1st/arithmetic-means/ps-arithmetic-means-input2}
}

\def \MasteryDay {\input{/storage/emulated/0/Documents/documents/latex/1920/Grade-10/1st/arithmetic-means/ps-arithmetic-means-input3}}

\def \ApplicationDay { Let the students answer the following questions: 
\begin{enumerate}[label = \arabic*. ]
%1
\item In what real life situations or problems can we observe some examples of arithmetic means? 
%2
\item How can you apply your knowledge of arithmetic means in solving these real life problems? 
%3
%\item 
\end{enumerate}   
}

\def \GeneralizationDay {Let the students answer the following questions: 
\begin{enumerate}[label = \arabic*. ]
%1
\item In your own words, what are arithmetic means? 
%2
\item How do we solve problems involving arithmetic means? 
%3
%\item 
\end{enumerate}   
}

\def \EvaluationDay {
\input{/storage/emulated/0/Documents/documents/latex/1920/Grade-10/1st/arithmetic-means/qz-arithmetic-means-input} 
}

\def \RemediationDay {}
