
\def \LessonDay {Adding and Subtracting Dissimilar Rational Algebraic Expressions}

\def \LearningCompetenciesDay {}

\def \ObjectivesDay {
\item Discuss the steps in adding and subtracting dissimilar rational algebraic expressions; 
\item Perform the steps in adding and subtracting dissimilar rational algebraic expressions; and, 
\item Exhibit willingness and interest in solving problems.
}

\def \PurposeDay {The purpose of this lesson is to enable the students to solve real life problems by adding and subtracting dissimilar rational algebraic expressions.}  

\def \ApplicationDay { Let the students answer the following questions: 
\begin{enumerate}[label = \arabic*. ]
%1
\item In what real life situations or problems can we observe some examples of adding and subtracting dissimilar rational algebraic expressions? 
%2
\item How can you apply your knowledge of adding and subtracting dissimilar rational algebraic expressions in solving these real life problems? 
\end{enumerate}   
}

\def \GeneralizationDay {Let the students answer the following questions: 
\begin{enumerate}[label = \arabic*. ]
%1
\item In your own words, how do we add or subtract dissimilar rational algebraic expressions? 
%2
\item How do we solve problems involving algebraic expressions that require adding and subtracting dissimilar rational algebraic expressions? 
\end{enumerate}   
}

\def \TeachersGuideDay {pp. 64--71}

\def \LMPagesDay {pp. 55--61}

\def \TextbookPagesDay {pp. 74--82}

\def \AdditionalMaterialsDay {}

\def \OtherResourcesDay {Flashcards}

\def \ReviewDay {\input{/storage/emulated/0/Documents/documents/latex/1920/Grade-8/1st/adding-and-subtracting-dissimilar-rational-algebraic-expressions/vs-adding-and-subtracting-dissimilar-rational-algebraic-expressions-input}}


\def \ExamplesDay {}

\def \PracticeOneDay {\input{/storage/emulated/0/Documents/documents/latex/1920/Grade-8/1st/adding-and-subtracting-dissimilar-rational-algebraic-expressions/ps-adding-and-subtracting-dissimilar-rational-algebraic-expressions-input1}}

\def \PracticeTwoDay {\input{/storage/emulated/0/Documents/documents/latex/1920/Grade-8/1st/adding-and-subtracting-dissimilar-rational-algebraic-expressions/ps-adding-and-subtracting-dissimilar-rational-algebraic-expressions-input2}
}

\def \MasteryDay {\input{/storage/emulated/0/Documents/documents/latex/1920/Grade-8/1st/adding-and-subtracting-dissimilar-rational-algebraic-expressions/ps-adding-and-subtracting-dissimilar-rational-algebraic-expressions-input3}}

\def \EvaluationDay {
\input{/storage/emulated/0/Documents/documents/latex/1920/Grade-8/1st/adding-and-subtracting-dissimilar-rational-algebraic-expressions/qz-adding-and-subtracting-dissimilar-rational-algebraic-expressions-input} 
}

\def \RemediationDay {}
