
\def \LessonDay {Complex Rational Expressions}

\def \LearningCompetenciesDay {}

\def \ObjectivesDay {
\item %cogverbstart
Reiterate 
%cogverbend
the steps in simplifying complex rational expressions; 
\item %psyverbstart
Simplify 
%psyverbend
complex rational expressions; and, 
\item %affverbstart
Project
%affverbend
%valsstart
willingness and self-reliance
%valsend
in solving problems.
}

\def \PurposeDay {The purpose of this lesson is to enable the students to solve real life problems involving  complex rational expressions.}  

\def \ApplicationDay { Let the students answer the following questions: 
\begin{enumerate}[label = \arabic*. ]
%1
\item In what real life situations or problems can we observe some examples of complex rational expressions? 
%2
\item How can you apply your knowledge of complex rational expressions in solving these real life problems? 
\end{enumerate}   
}

\def \GeneralizationDay {Let the students answer the following questions: 
\begin{enumerate}[label = \arabic*. ]
%1
\item In your own words, what are complex rational expressions? 
%2
\item How do we solve problems involving algebraic expressions that require complex rational expressions? 
\end{enumerate}   
}

\def \TeachersGuideDay {pp. 211--223}

\def \LMPagesDay {pp. 228--242}

\def \TextbookPagesDay {pp. 250--265}

\def \AdditionalMaterialsDay {}

\def \OtherResourcesDay {Flashcards}

\def \ReviewDay {\input{/storage/emulated/0/Documents/documents/latex/1920/Grade-8/1st/complex-rational-expressions/vs-complex-rational-expressions-input}}


\def \ExamplesDay {}

\def \PracticeOneDay {\input{/storage/emulated/0/Documents/documents/latex/1920/Grade-8/1st/complex-rational-expressions/ps-complex-rational-expressions-input1}}

\def \PracticeTwoDay {\input{/storage/emulated/0/Documents/documents/latex/1920/Grade-8/1st/complex-rational-expressions/ps-complex-rational-expressions-input2}
}

\def \MasteryDay {\input{/storage/emulated/0/Documents/documents/latex/1920/Grade-8/1st/complex-rational-expressions/ps-complex-rational-expressions-input3}}

\def \EvaluationDay {
\input{/storage/emulated/0/Documents/documents/latex/1920/Grade-8/1st/complex-rational-expressions/qz-complex-rational-expressions-input} 
}

\def \RemediationDay {}
