% cd ~/storage/emulated/0/Documents/documents/latex/1920/Grade-10/2nd/distance-formula/ && pdflatex semi-lp-distance-formula.tex && ula-open semi-lp-distance-formula.pdf


\documentclass[12pt]{article}
\usepackage[legalpaper, portrait, right=0.5in,  left=0.5in, top=0.5in, bottom=1.5in]{geometry}

\input{/host-rootfs/storage/emulated/0/Documents/documents/latex/1920/common-preamble-2019} 

\def \Grade {10
}

\def \Teacher {
Mr. Jonathan R. Bacolod, LPT 
}

\def \Module {
Geometry 
}

\def \Date {
Oct 8, 2019 
}

\def \ContentStandard {
The learner demonstrates understanding of key concepts of circles and coordinate geometry.   
}

\def \PerformanceStandard {
The learner is able to formulate and find solutions to challenging situations involving circles and other related terms in different disciplines through appropriate and accurate representations.
}

\def \LearningCompetency {
The learner applies the distance formula to prove some geometric properties. (M10GE-IIg-2)
}

\def \Objectives {
\item Describe the distance formula; 
\item Prove some geometric properties using the distance formula; and, 
\item Show interest and perseverance in solving problems. 
}

\def \Generalization {
\item[a. ] In your own words, what is the distance formula?    
\item[b. ] How do we solve problems involving the  distance formula? 
}


\def \Topic {
Distance Formula 
}

\def \ReviewTopic {
Area of Sectors and Segments of a Circle   
}

\def \Motivation {
}

\def \Reference {
Mathematics \Grade Learner’s Module pp. 229-237
}

\def \Materials {
Handouts showing the steps and the formula for the \Topic
}

\def \Checker {
\underline{\textbf{DR. LORETO R. DOMINGO}}\\
OIC/MT II Mathematics Department
}

\def \DirectInstruction {
\input{vs-distance-formula-input}
}

\def \PE {
\input{ps-distance-formula-input1} 
}

\def \PS {
\input{ps-distance-formula-input3}
}


\begin{document}

\input{/host-rootfs/storage/emulated/0/Documents/documents/latex/1920/semi-detailed-lp-format-2019} 

\end{document}