
\def \LessonDay {Geometric Means}

\def \LearningCompetenciesDay {}

\def \ObjectivesDay {
\item Describe the steps in finding the geometric mean; 
\item Compute the geometric mean  of a given geometric sequence; and, 
\item Show enjoyment and perseverance in solving problems.
}

\def \PurposeDay {The purpose of this lesson is to enable the students to solve real life problems involving geometric means.}  

\def \ApplicationDay { Let the students answer the following questions: 
\begin{enumerate}[label = \arabic*. ]
%1
\item In what real life situations or problems can we observe some examples of geometric means? 
%2
\item How can you apply your knowledge of geometric means in solving these real life problems? 

\end{enumerate}   
}

\def \GeneralizationDay {Let the students answer the following questions: 
\begin{enumerate}[label = \arabic*. ]
%1
\item In your own words, what are geometric means? 
%2
\item How do we solve problems involving geometric means? 

\end{enumerate}   
}

\def \TeachersGuideDay {pp. 72--82}

\def \LMPagesDay {pp. 43--49}

\def \TextbookPagesDay {pp. 60--69}

\def \AdditionalMaterialsDay {}

\def \OtherResourcesDay {Flashcards}

\def \ReviewDay {\input{/storage/emulated/0/Documents/documents/latex/1920/Grade-10/1st/geometric-means/vs-geometric-means-input}}



\def \ExamplesDay {}

\def \PracticeOneDay {\input{/storage/emulated/0/Documents/documents/latex/1920/Grade-10/1st/geometric-means/ps-geometric-means-input1}}

\def \PracticeTwoDay {\input{/storage/emulated/0/Documents/documents/latex/1920/Grade-10/1st/geometric-means/ps-geometric-means-input2}
}

\def \MasteryDay {\input{/storage/emulated/0/Documents/documents/latex/1920/Grade-10/1st/geometric-means/ps-geometric-means-input3}}



\def \EvaluationDay {
\input{/storage/emulated/0/Documents/documents/latex/1920/Grade-10/1st/geometric-means/qz-geometric-means-input} 
}

\def \RemediationDay {}
