
\def \LessonDay {Infinite Geometric Series}

\def \LearningCompetenciesDay {}

\def \ObjectivesDay {
\item Tell the steps in finding the sum of the terms of an infinite geometric sequence; 
\item Generate the sum of the terms of an infinite geometric sequence; and, 
\item Display willingness and interest in solving problems.
}

\def \TeachersGuideDay {pp. 63--71}

\def \LMPagesDay {pp. 38--42}

\def \TextbookPagesDay {pp. 53--59}

\def \AdditionalMaterialsDay {}

\def \OtherResourcesDay {Flashcards}

\def \ReviewDay {\input{/storage/emulated/0/Documents/documents/latex/1920/Grade-10/1st/infinite-geometric-series/vs-infinite-geometric-series-input}}

\def \PurposeDay {The purpose of this lesson is to enable the students to solve real life problems involving infinite geometric series.}  

\def \ExamplesDay {Some examples of infinite geometric series are the following: 
\begin{enumerate}[label = \arabic*. ]
%1
\item The sum of even integers from 5 to 11 is 24.
%2
\item $1 + 3 + 5 + 7 = 16$
%3
%\item 
\end{enumerate}   
}

\def \PracticeOneDay {\input{/storage/emulated/0/Documents/documents/latex/1920/Grade-10/1st/infinite-geometric-series/ps-infinite-geometric-series-input1}}

\def \PracticeTwoDay {\input{/storage/emulated/0/Documents/documents/latex/1920/Grade-10/1st/infinite-geometric-series/ps-infinite-geometric-series-input2}
}

\def \MasteryDay {\input{/storage/emulated/0/Documents/documents/latex/1920/Grade-10/1st/infinite-geometric-series/ps-infinite-geometric-series-input3}}

\def \ApplicationDay { Let the students answer the following questions: 
\begin{enumerate}[label = \arabic*. ]
%1
\item In what real life situations or problems can we observe some examples of infinite geometric series? 
%2
\item How can you apply your knowledge of infinite geometric series in solving these real life problems? 
%3
%\item 
\end{enumerate}   
}

\def \GeneralizationDay {Let the students answer the following questions: 
\begin{enumerate}[label = \arabic*. ]
%1
\item In your own words, what are infinite geometric series? 
%2
\item How do we solve problems involving infinite geometric series? 
%3
%\item 
\end{enumerate}   
}

\def \EvaluationDay {
\input{/storage/emulated/0/Documents/documents/latex/1920/Grade-10/1st/infinite-geometric-series/qz-infinite-geometric-series-input} 
}

\def \RemediationDay {}
