%\textbf{Practice Exercises}
\textbf{Problem Set}

\vspce

Solve each problem completely.
\begin{enumerate}[label = \arabic*. ]
%1
\item Anabelle would like to invite 9 friends to go on a trip but has room for only 5 of them. In how many ways can they be chosen?
%2
\item A box with 12 articles contains one that is defective. In how many ways can Martin
select 5 articles such that: 
\begin{enumerate}[label = \alph*. ]
%A
\item the defective article is included?
%B
\item the defective article is not included?
\end{enumerate}  
%3
\item A box contains 8 blue balls, 6 white balls, and 4 black balls. In how many ways can we select 4 balls such that: 
\begin{enumerate}[label = \alph*. ]
%A
%\item they are blue?
%B
\item they are all white?
%C
%\item they are all black?
%d
\item two are blue, one is white, and one is black?
%e
\item exactly 2 are black?
%f
%\item exactly 1 is black?
%g
\item none is blue?
\end{enumerate}  
%4
%\item How many subcommittees of 5 people can be formed from a committee consisting of 8 people?
%5
\item A group of 11 women and 6 men must select a four-person committee. How many committees are possible if it must consist of the following?
\begin{enumerate}[label = \alph*. ]
%A
\item three men and one woman
%B
\item any mixture of men and women
%C
\item a man and three women
%\item a majority of men
\end{enumerate}  
%6
\item A class consists of 12 boys and 15 girls. How many different committees of four can be selected from the class if each committee is to consist of two boys and two girls?
%7
\item How many choices of 5 pocketbooks to read can be made from a set of nine pocketbooks?

\end{enumerate}   

