\textbf{Problem Set}

\vspce

A. Find the number of possible outcomes for each scenario using the tree diagram and the fundamental counting principle. 
 
\begin{enumerate}[label = \arabic*. ]

%6
\item Clocks come in 2 styles: wall or desk. They come in 5 colors: white, black, red, blue, or orange.
%7
\item Basketball uniform in white, red, or green which comes in sizes small, medium, or large.
%8
\item A coin is tossed three times.
%9
\item A coin is tossed  and a die is rolled. 
%10
\item Notebooks come in 4 colors: red, yellow, green, and blue. They come in 2 types: 5-subject and 7-subject.
\end{enumerate}   
 
B. Solve each problem completely. 

\begin{enumerate}[label = \arabic*. ]

\item  A restaurant offers four sizes of pizza, two types of crust, and eight toppings. How many possible combinations of pizza with one topping are there? 
\item  How many ways can 5 paintings be lined up on a wall? 
\item  Rob has 4 shirts, 3 pairs of pants, and 2 pairs of shoes that all coordinate. How many 
outfits can you put together? 
\item  Grace loves to eat salad! How many salads can she put together if she can pick out one type of lettuce from 2 choices, one vegetable from 4 choices and one dressing from 7 choices? 
\item  Motorcycle license plates have 2 letters followed by 4 numbers. 
\begin{enumerate}[label = \alph*. ]
%a
\item If the same letter or number can be repeated, how many can be made?
%b
\item If the same letter CANNOT be repeated, how many can be made?
%c
%\item 
\end{enumerate} 
 
\item  How many 5-digit numbers can be formed (using 0 – 9)? 
\item  How many 5-digit numbers can be formed if each one uses all the digits 0, 1, 2, 3, 4 
without repetition? 
\item  In how many ways can 6 bicycles be parked in a row? 

\end{enumerate} 