 

\def \LessonDayA {Evaluating Rational Expressions}

\def \LearningCompetenciesDayA {}

\def \ObjectivesDayA {
\item Reiterate the steps in evaluating rational expressions; 
\item Evaluate rational algebraic expressions; and, 
\item Show independence and perseverance in solving problems.
}

\def \PurposeDayA {The purpose of this lesson is to enable the students to solve real life problems involving evaluating rational expressions.}  

\def \ApplicationDayA { Let the students answer the following questions: 
\begin{enumerate}[label = \arabic*. ]
%1
\item In what real life situations or problems can we observe some examples of evaluating rational expressions? 
%2
\item How can you apply your knowledge of evaluating rational expressions in solving these real life problems? 
\end{enumerate}   
}

\def \GeneralizationDayA {Let the students answer the following questions: 
\begin{enumerate}[label = \arabic*. ]
%1
\item In your own words, how do we evaluate rational expressions? 
%2
\item How do we solve problems involving algebraic expressions that require evaluating rational expressions? 
\end{enumerate}   
}

\def \TeachersGuideDayA {pp. 64--71}

\def \LMPagesDayA {pp. 55--61}

\def \TextbookPagesDayA {pp. 74--82}

\def \AdditionalMaterialsDayA {}

\def \OtherResourcesDayA {Flashcards}

\def \ReviewDayA {\input{/host-rootfs/storage/emulated/0/Documents/documents/latex/1920/Grade-8/1st/evaluating-rational-expressions/vs-evaluating-rational-expressions-input}}


\def \ExamplesDayA {}

\def \PracticeOneDayA {\input{/host-rootfs/storage/emulated/0/Documents/documents/latex/1920/Grade-8/1st/evaluating-rational-expressions/ps-evaluating-rational-expressions-input1}}

\def \PracticeTwoDayA {\input{/host-rootfs/storage/emulated/0/Documents/documents/latex/1920/Grade-8/1st/evaluating-rational-expressions/ps-evaluating-rational-expressions-input2}
}

\def \MasteryDayA {\input{/host-rootfs/storage/emulated/0/Documents/documents/latex/1920/Grade-8/1st/evaluating-rational-expressions/ps-evaluating-rational-expressions-input3}}

\def \EvaluationDayA {
\input{/host-rootfs/storage/emulated/0/Documents/documents/latex/1920/Grade-8/1st/evaluating-rational-expressions/qz-evaluating-rational-expressions-input} 
}

\def \RemediationDayA {}

\def \LessonDayB {Multiplying Rational Algebraic Expressions}

\def \LearningCompetenciesDayB {}

\def \ObjectivesDayB {
\item Restate the steps in multiplying rational algebraic expressions; 
\item Find the product of rational algebraic expressions; and, 
\item Show perseverance and willingness in solving problems.
}

\def \PurposeDayB {The purpose of this lesson is to enable the students to solve real life problems by multiplying rational algebraic expressions.}  

\def \ApplicationDayB { Let the students answer the following questions: 
\begin{enumerate}[label = \arabic*. ]
%1
\item In what real life situations or problems can we observe some examples of multiplying rational algebraic expressions? 
%2
\item How can you apply your knowledge of multiplying rational algebraic expressions in solving these real life problems? 
\end{enumerate}   
}

\def \GeneralizationDayB {Let the students answer the following questions: 
\begin{enumerate}[label = \arabic*. ]
%1
\item In your own words, how do we multiply rational algebraic expressions? 
%2
\item How do we solve problems involving algebraic expressions that require multiplying rational algebraic expressions? 
\end{enumerate}   
}

\def \TeachersGuideDayB {pp. 114--124}

\def \LMPagesDayB {pp. 98--112}

\def \TextbookPagesDayB {pp. 131--140}

\def \AdditionalMaterialsDayB {}

\def \OtherResourcesDayB {Flashcards}

\def \ReviewDayB {\input{/host-rootfs/storage/emulated/0/Documents/documents/latex/1920/Grade-8/1st/multiplying-rational-algebraic-expressions/vs-multiplying-rational-algebraic-expressions-input}}


\def \ExamplesDayB {}

\def \PracticeOneDayB {\input{/host-rootfs/storage/emulated/0/Documents/documents/latex/1920/Grade-8/1st/multiplying-rational-algebraic-expressions/ps-multiplying-rational-algebraic-expressions-input1}}

\def \PracticeTwoDayB {\input{/host-rootfs/storage/emulated/0/Documents/documents/latex/1920/Grade-8/1st/multiplying-rational-algebraic-expressions/ps-multiplying-rational-algebraic-expressions-input2}
}

\def \MasteryDayB {\input{/host-rootfs/storage/emulated/0/Documents/documents/latex/1920/Grade-8/1st/multiplying-rational-algebraic-expressions/ps-multiplying-rational-algebraic-expressions-input3}}

\def \EvaluationDayB {
\input{/host-rootfs/storage/emulated/0/Documents/documents/latex/1920/Grade-8/1st/multiplying-rational-algebraic-expressions/qz-multiplying-rational-algebraic-expressions-input} 
}

\def \RemediationDayB {}

\def \LessonDayC {Dividing Rational Algebraic Expressions}

\def \LearningCompetenciesDayC {}

\def \ObjectivesDayC {
\item %cogverbstart
Execute 
%cogverbend
the steps in dividing rational algebraic expressions; 
\item %psyverbstart
Find 
%psyverbend
the product of rational algebraic expressions; and, 
\item %affverbstart
Show 
%affverbend
%valsstart
perseverance and interest 
%valsend
in solving problems.
}

\def \PurposeDayC {The purpose of this lesson is to enable the students to solve real life problems by dividing rational algebraic expressions.}  

\def \ApplicationDayC { Let the students answer the following questions: 
\begin{enumerate}[label = \arabic*. ]
%1
\item In what real life situations or problems can we observe some examples of dividing rational algebraic expressions? 
%2
\item How can you apply your knowledge of dividing rational algebraic expressions in solving these real life problems? 
\end{enumerate}   
}

\def \GeneralizationDayC {Let the students answer the following questions: 
\begin{enumerate}[label = \arabic*. ]
%1
\item In your own words, how do we multiply rational algebraic expressions? 
%2
\item How do we solve problems involving algebraic expressions that require dividing rational algebraic expressions? 
\end{enumerate}   
}

\def \TeachersGuideDayC {pp. 189--201}

\def \LMPagesDayC {pp. 206--218}

\def \TextbookPagesDayC {pp. 224--237}

\def \AdditionalMaterialsDayC {}

\def \OtherResourcesDayC {Flashcards}

\def \ReviewDayC {\input{/host-rootfs/storage/emulated/0/Documents/documents/latex/1920/Grade-8/1st/dividing-rational-algebraic-expressions/vs-dividing-rational-algebraic-expressions-input}}


\def \ExamplesDayC {}

\def \PracticeOneDayC {\input{/host-rootfs/storage/emulated/0/Documents/documents/latex/1920/Grade-8/1st/dividing-rational-algebraic-expressions/ps-dividing-rational-algebraic-expressions-input1}}

\def \PracticeTwoDayC {\input{/host-rootfs/storage/emulated/0/Documents/documents/latex/1920/Grade-8/1st/dividing-rational-algebraic-expressions/ps-dividing-rational-algebraic-expressions-input2}
}

\def \MasteryDayC {\input{/host-rootfs/storage/emulated/0/Documents/documents/latex/1920/Grade-8/1st/dividing-rational-algebraic-expressions/ps-dividing-rational-algebraic-expressions-input3}}

\def \EvaluationDayC {
\input{/host-rootfs/storage/emulated/0/Documents/documents/latex/1920/Grade-8/1st/dividing-rational-algebraic-expressions/qz-dividing-rational-algebraic-expressions-input} 
}

\def \RemediationDayC {}

\def \LessonDayD {Adding and Subtracting Similar Rational Algebraic Expressions}

\def \LearningCompetenciesDayD {}

\def \ObjectivesDayD {
\item Describe the steps in adding and subtracting similar rational algebraic expressions; 
\item Perform the steps in adding and subtracting similar rational algebraic expressions; and, 
\item Project independence and willingness in solving problems.
}

\def \PurposeDayD {The purpose of this lesson is to enable the students to solve real life problems by adding and subtracting similar rational algebraic expressions.}  

\def \ApplicationDayD { Let the students answer the following questions: 
\begin{enumerate}[label = \arabic*. ]
%1
\item In what real life situations or problems can we observe some examples of adding and subtracting similar rational algebraic expressions? 
%2
\item How can you apply your knowledge of adding and subtracting similar rational algebraic expressions in solving these real life problems? 
\end{enumerate}   
}

\def \GeneralizationDayD {Let the students answer the following questions: 
\begin{enumerate}[label = \arabic*. ]
%1
\item In your own words, how do we add or subtract similar rational algebraic expressions? 
%2
\item How do we solve problems involving algebraic expressions that require adding and subtracting similar rational algebraic expressions? 
\end{enumerate}   
}

\def \TeachersGuideDayD {pp. 100--105}

\def \LMPagesDayD {pp. 86--90}

\def \TextbookPagesDayD {pp. 115--121}

\def \AdditionalMaterialsDayD {}

\def \OtherResourcesDayD {Flashcards}

\def \ReviewDayD {\input{/host-rootfs/storage/emulated/0/Documents/documents/latex/1920/Grade-8/1st/adding-and-subtracting-similar-rational-algebraic-expressions/vs-adding-and-subtracting-similar-rational-algebraic-expressions-input}}


\def \ExamplesDayD {}

\def \PracticeOneDayD {\input{/host-rootfs/storage/emulated/0/Documents/documents/latex/1920/Grade-8/1st/adding-and-subtracting-similar-rational-algebraic-expressions/ps-adding-and-subtracting-similar-rational-algebraic-expressions-input1}}

\def \PracticeTwoDayD {\input{/host-rootfs/storage/emulated/0/Documents/documents/latex/1920/Grade-8/1st/adding-and-subtracting-similar-rational-algebraic-expressions/ps-adding-and-subtracting-similar-rational-algebraic-expressions-input2}
}

\def \MasteryDayD {\input{/host-rootfs/storage/emulated/0/Documents/documents/latex/1920/Grade-8/1st/adding-and-subtracting-similar-rational-algebraic-expressions/ps-adding-and-subtracting-similar-rational-algebraic-expressions-input3}}

\def \EvaluationDayD {
\input{/host-rootfs/storage/emulated/0/Documents/documents/latex/1920/Grade-8/1st/adding-and-subtracting-similar-rational-algebraic-expressions/qz-adding-and-subtracting-similar-rational-algebraic-expressions-input} 
}

\def \RemediationDayD {}

\def \LessonDayE {Adding and Subtracting Dissimilar Rational Algebraic Expressions}

\def \LearningCompetenciesDayE {}

\def \ObjectivesDayE {
\item Discuss the steps in adding and subtracting dissimilar rational algebraic expressions; 
\item Perform the steps in adding and subtracting dissimilar rational algebraic expressions; and, 
\item Exhibit willingness and interest in solving problems.
}

\def \PurposeDayE {The purpose of this lesson is to enable the students to solve real life problems by adding and subtracting dissimilar rational algebraic expressions.}  

\def \ApplicationDayE { Let the students answer the following questions: 
\begin{enumerate}[label = \arabic*. ]
%1
\item In what real life situations or problems can we observe some examples of adding and subtracting dissimilar rational algebraic expressions? 
%2
\item How can you apply your knowledge of adding and subtracting dissimilar rational algebraic expressions in solving these real life problems? 
\end{enumerate}   
}

\def \GeneralizationDayE {Let the students answer the following questions: 
\begin{enumerate}[label = \arabic*. ]
%1
\item In your own words, how do we add or subtract dissimilar rational algebraic expressions? 
%2
\item How do we solve problems involving algebraic expressions that require adding and subtracting dissimilar rational algebraic expressions? 
\end{enumerate}   
}

\def \TeachersGuideDayE {pp. 64--71}

\def \LMPagesDayE {pp. 55--61}

\def \TextbookPagesDayE {pp. 74--82}

\def \AdditionalMaterialsDayE {}

\def \OtherResourcesDayE {Flashcards}

\def \ReviewDayE {\input{/host-rootfs/storage/emulated/0/Documents/documents/latex/1920/Grade-8/1st/adding-and-subtracting-dissimilar-rational-algebraic-expressions/vs-adding-and-subtracting-dissimilar-rational-algebraic-expressions-input}}


\def \ExamplesDayE {}

\def \PracticeOneDayE {\input{/host-rootfs/storage/emulated/0/Documents/documents/latex/1920/Grade-8/1st/adding-and-subtracting-dissimilar-rational-algebraic-expressions/ps-adding-and-subtracting-dissimilar-rational-algebraic-expressions-input1}}

\def \PracticeTwoDayE {\input{/host-rootfs/storage/emulated/0/Documents/documents/latex/1920/Grade-8/1st/adding-and-subtracting-dissimilar-rational-algebraic-expressions/ps-adding-and-subtracting-dissimilar-rational-algebraic-expressions-input2}
}

\def \MasteryDayE {\input{/host-rootfs/storage/emulated/0/Documents/documents/latex/1920/Grade-8/1st/adding-and-subtracting-dissimilar-rational-algebraic-expressions/ps-adding-and-subtracting-dissimilar-rational-algebraic-expressions-input3}}

\def \EvaluationDayE {
\input{/host-rootfs/storage/emulated/0/Documents/documents/latex/1920/Grade-8/1st/adding-and-subtracting-dissimilar-rational-algebraic-expressions/qz-adding-and-subtracting-dissimilar-rational-algebraic-expressions-input} 
}

\def \RemediationDayE {}
