 

\def \LessonDayA {Factoring the Sum or Difference of Two Cubes}

\def \LearningCompetenciesDayA {}

\def \ObjectivesDayA {
\item Identify the cube roots of algebraic expressions; 
\item Find the factors of the sum or difference of two cubes; and, 
\item Show independence and independence in solving problems.
}

\def \PurposeDayA {The purpose of this lesson is to enable the students to solve real life problems by factoring the sum or difference of two cubes.}  

\def \ApplicationDayA { Let the students answer the following questions: 
\begin{enumerate}[label = \arabic*. ]
%1
\item In what real life situations or problems can we observe some examples of factoring  the sum or difference of two cubes? 
%2
\item How can you apply your knowledge of factoring the sum or difference of two cubes in solving these real life problems? 
\end{enumerate}   
}

\def \GeneralizationDayA {Let the students answer the following questions: 
\begin{enumerate}[label = \arabic*. ]
%1
\item In your own words, how do we find the  factors of the sum or difference of two cubes? 
%2
\item How do we solve problems involving algebraic expressions that require  factoring the sum or difference of two cubes? 
\end{enumerate}   
}

\def \TeachersGuideDayA {pp. 44--49}

\def \LMPagesDayA {pp. 38--42}

\def \TextbookPagesDayA {pp. 50--56}

\def \AdditionalMaterialsDayA {}

\def \OtherResourcesDayA {Flashcards}

\def \ReviewDayA {\input{/host-rootfs/storage/emulated/0/Documents/documents/latex/1920/Grade-8/1st/factoring-the-sum-or-difference-of-two-cubes/vs-factoring-the-sum-or-difference-of-two-cubes-input}}


\def \ExamplesDayA {}

\def \PracticeOneDayA {\input{/host-rootfs/storage/emulated/0/Documents/documents/latex/1920/Grade-8/1st/factoring-the-sum-or-difference-of-two-cubes/ps-factoring-the-sum-or-difference-of-two-cubes-input1}}

\def \PracticeTwoDayA {\input{/host-rootfs/storage/emulated/0/Documents/documents/latex/1920/Grade-8/1st/factoring-the-sum-or-difference-of-two-cubes/ps-factoring-the-sum-or-difference-of-two-cubes-input2}
}

\def \MasteryDayA {\input{/host-rootfs/storage/emulated/0/Documents/documents/latex/1920/Grade-8/1st/factoring-the-sum-or-difference-of-two-cubes/ps-factoring-the-sum-or-difference-of-two-cubes-input3}}

\def \EvaluationDayA {
\input{/host-rootfs/storage/emulated/0/Documents/documents/latex/1920/Grade-8/1st/factoring-the-sum-or-difference-of-two-cubes/qz-factoring-the-sum-or-difference-of-two-cubes-input} 
}

\def \RemediationDayA {}

\def \LessonDayB {Factoring Perfect Square Trinomials}

\def \LearningCompetenciesDayB {}

\def \ObjectivesDayB {
\item State the steps in factoring perfect square trinomials; 
\item Calculate the square roots of given  algebraic expressions; and, 
\item Display independence and independence in solving problems.
}

\def \PurposeDayB {The purpose of this lesson is to enable the students to solve real life problems by factoring perfect square trinomials.}  

\def \ApplicationDayB { Let the students answer the following questions: 
\begin{enumerate}[label = \arabic*. ]
%1
\item In what real life situations or problems can we observe some examples of factoring perfect square trinomials? 
%2
\item How can you apply your knowledge of factoring perfect square trinomials in solving these real life problems? 
\end{enumerate}   
}

\def \GeneralizationDayB {Let the students answer the following questions: 
\begin{enumerate}[label = \arabic*. ]
%1
\item In your own words, how do we  factor perfect square trinomials? 
%2
\item How do we solve problems involving algebraic expressions that require  factoring perfect square trinomials? 
\end{enumerate}   
}

\def \TeachersGuideDayB {pp. 50--57}

\def \LMPagesDayB {pp. 43--49}

\def \TextbookPagesDayB {pp. 57--66}

\def \AdditionalMaterialsDayB {}

\def \OtherResourcesDayB {Flashcards}

\def \ReviewDayB {\input{/host-rootfs/storage/emulated/0/Documents/documents/latex/1920/Grade-8/1st/factoring-perfect-square-trinomials/vs-factoring-perfect-square-trinomials-input}}


\def \ExamplesDayB {}

\def \PracticeOneDayB {\input{/host-rootfs/storage/emulated/0/Documents/documents/latex/1920/Grade-8/1st/factoring-perfect-square-trinomials/ps-factoring-perfect-square-trinomials-input1}}

\def \PracticeTwoDayB {\input{/host-rootfs/storage/emulated/0/Documents/documents/latex/1920/Grade-8/1st/factoring-perfect-square-trinomials/ps-factoring-perfect-square-trinomials-input2}
}

\def \MasteryDayB {\input{/host-rootfs/storage/emulated/0/Documents/documents/latex/1920/Grade-8/1st/factoring-perfect-square-trinomials/ps-factoring-perfect-square-trinomials-input3}}

\def \EvaluationDayB {
\input{/host-rootfs/storage/emulated/0/Documents/documents/latex/1920/Grade-8/1st/factoring-perfect-square-trinomials/qz-factoring-perfect-square-trinomials-input} 
}

\def \RemediationDayB {}

\def \LessonDayC {Factoring Trinomials with 1 as Leading Coefficient}

\def \LearningCompetenciesDayC {}

\def \ObjectivesDayC {
\item Tell the steps in factoring trinomials with 1 as leading coefficient; 
\item Compute the factors of  trinomials with 1 as leading coefficient; and, 
\item Project enjoyment and enjoyment in solving problems.
}

\def \PurposeDayC {The purpose of this lesson is to enable the students to solve real life problems by factoring trinomials with 1 as leading coefficient.}  

\def \ApplicationDayC { Let the students answer the following questions: 
\begin{enumerate}[label = \arabic*. ]
%1
\item In what real life situations or problems can we observe some examples of factoring trinomials with 1 as leading coefficient? 
%2
\item How can you apply your knowledge of factoring trinomials with 1 as leading coefficient in solving these real life problems? 
\end{enumerate}   
}

\def \GeneralizationDayC {Let the students answer the following questions: 
\begin{enumerate}[label = \arabic*. ]
%1
\item In your own words, how do we  factor trinomials with 1 as leading coefficient? 
%2
\item How do we solve problems involving algebraic expressions that require  factoring trinomials with 1 as leading coefficient? 
\end{enumerate}   
}

\def \TeachersGuideDayC {pp. 58--63}

\def \LMPagesDayC {pp. 50--54}

\def \TextbookPagesDayC {pp. 67--73}

\def \AdditionalMaterialsDayC {}

\def \OtherResourcesDayC {Flashcards}

\def \ReviewDayC {\input{/host-rootfs/storage/emulated/0/Documents/documents/latex/1920/Grade-8/1st/factoring-trinomials-with-1-as-leading-coefficient/vs-factoring-trinomials-with-1-as-leading-coefficient-input}}


\def \ExamplesDayC {}

\def \PracticeOneDayC {\input{/host-rootfs/storage/emulated/0/Documents/documents/latex/1920/Grade-8/1st/factoring-trinomials-with-1-as-leading-coefficient/ps-factoring-trinomials-with-1-as-leading-coefficient-input1}}

\def \PracticeTwoDayC {\input{/host-rootfs/storage/emulated/0/Documents/documents/latex/1920/Grade-8/1st/factoring-trinomials-with-1-as-leading-coefficient/ps-factoring-trinomials-with-1-as-leading-coefficient-input2}
}

\def \MasteryDayC {\input{/host-rootfs/storage/emulated/0/Documents/documents/latex/1920/Grade-8/1st/factoring-trinomials-with-1-as-leading-coefficient/ps-factoring-trinomials-with-1-as-leading-coefficient-input3}}

\def \EvaluationDayC {
\input{/host-rootfs/storage/emulated/0/Documents/documents/latex/1920/Grade-8/1st/factoring-trinomials-with-1-as-leading-coefficient/qz-factoring-trinomials-with-1-as-leading-coefficient-input} 
}

\def \RemediationDayC {}

\def \LessonDayD {Factoring by Grouping}

\def \LearningCompetenciesDayD {}

\def \ObjectivesDayD {
\item Distinguish the steps in factoring by grouping with factoring the greatest common monomial factor; 
\item Solve the factors of an algebraic expression using the grouping method; and, 
\item Demonstrate willingness and willingness in solving problems.
}

\def \PurposeDayD {The purpose of this lesson is to enable the students to solve real life problems by using factoring by grouping.}  

\def \ApplicationDayD { Let the students answer the following questions: 
\begin{enumerate}[label = \arabic*. ]
%1
\item In what real life situations or problems can we observe some examples of factoring by grouping? 
%2
\item How can you apply your knowledge of factoring by grouping in solving these real life problems? 
\end{enumerate}   
}

\def \GeneralizationDayD {Let the students answer the following questions: 
\begin{enumerate}[label = \arabic*. ]
%1
\item In your own words, how do we  factor  by grouping? 
%2
\item How do we solve problems involving algebraic expressions that require  factoring by grouping? 
\end{enumerate}   
}

\def \TeachersGuideDayD {pp. 72--77}

\def \LMPagesDayD {pp. 62--66}

\def \TextbookPagesDayD {pp. 83--89}

\def \AdditionalMaterialsDayD {}

\def \OtherResourcesDayD {Flashcards}

\def \ReviewDayD {\input{/host-rootfs/storage/emulated/0/Documents/documents/latex/1920/Grade-8/1st/factoring-by-grouping/vs-factoring-by-grouping-input}}


\def \ExamplesDayD {}

\def \PracticeOneDayD {\input{/host-rootfs/storage/emulated/0/Documents/documents/latex/1920/Grade-8/1st/factoring-by-grouping/ps-factoring-by-grouping-input1}}

\def \PracticeTwoDayD {\input{/host-rootfs/storage/emulated/0/Documents/documents/latex/1920/Grade-8/1st/factoring-by-grouping/ps-factoring-by-grouping-input2}
}

\def \MasteryDayD {\input{/host-rootfs/storage/emulated/0/Documents/documents/latex/1920/Grade-8/1st/factoring-by-grouping/ps-factoring-by-grouping-input3}}

\def \EvaluationDayD {
\input{/host-rootfs/storage/emulated/0/Documents/documents/latex/1920/Grade-8/1st/factoring-by-grouping/qz-factoring-by-grouping-input} 
}

\def \RemediationDayD {}

\def \LessonDayE {Factoring General Trinomials}

\def \LearningCompetenciesDayE {}

\def \ObjectivesDayE {
\item Define the steps in factoring general trinomials; 
\item Calculate the factors of  general trinomials; and, 
\item Display perseverance and perseverance in solving problems.
}

\def \PurposeDayE {The purpose of this lesson is to enable the students to solve real life problems by factoring general trinomials.}  

\def \ApplicationDayE { Let the students answer the following questions: 
\begin{enumerate}[label = \arabic*. ]
%1
\item In what real life situations or problems can we observe some examples of factoring general trinomials? 
%2
\item How can you apply your knowledge of factoring general trinomials in solving these real life problems? 
\end{enumerate}   
}

\def \GeneralizationDayE {Let the students answer the following questions: 
\begin{enumerate}[label = \arabic*. ]
%1
\item In your own words, how do we  factor general trinomials? 
%2
\item How do we solve problems involving algebraic expressions that require  factoring general trinomials? 
\end{enumerate}   
}

\def \TeachersGuideDayE {pp. 64--71}

\def \LMPagesDayE {pp. 55--61}

\def \TextbookPagesDayE {pp. 74--82}

\def \AdditionalMaterialsDayE {}

\def \OtherResourcesDayE {Flashcards}

\def \ReviewDayE {\input{/host-rootfs/storage/emulated/0/Documents/documents/latex/1920/Grade-8/1st/factoring-general-trinomials/vs-factoring-general-trinomials-input}}


\def \ExamplesDayE {}

\def \PracticeOneDayE {\input{/host-rootfs/storage/emulated/0/Documents/documents/latex/1920/Grade-8/1st/factoring-general-trinomials/ps-factoring-general-trinomials-input1}}

\def \PracticeTwoDayE {\input{/host-rootfs/storage/emulated/0/Documents/documents/latex/1920/Grade-8/1st/factoring-general-trinomials/ps-factoring-general-trinomials-input2}
}

\def \MasteryDayE {\input{/host-rootfs/storage/emulated/0/Documents/documents/latex/1920/Grade-8/1st/factoring-general-trinomials/ps-factoring-general-trinomials-input3}}

\def \EvaluationDayE {
\input{/host-rootfs/storage/emulated/0/Documents/documents/latex/1920/Grade-8/1st/factoring-general-trinomials/qz-factoring-general-trinomials-input} 
}

\def \RemediationDayE {}
