 

\def \LessonDayA {Fibonacci Sequence}

\def \LearningCompetenciesDayA {}

\def \ObjectivesDayA {
\item Describe the steps in finding the next terms of a  fibonacci sequence; 
\item Solve the next terms of a  fibonacci sequence; and, 
\item Show willingness and interest in solving problems.
}

\def \PurposeDayA {The purpose of this lesson is to enable the students to solve real life problems involving fibonacci sequence.}  

\def \ApplicationDayA { Let the students answer the following questions: 
\begin{enumerate}[label = \arabic*. ]
%1
\item In what real life situations or problems can we observe some examples of fibonacci sequence? 
%2
\item How can you apply your knowledge of fibonacci sequence in solving these real life problems? 

\end{enumerate}   
}

\def \GeneralizationDayA {Let the students answer the following questions: 
\begin{enumerate}[label = \arabic*. ]
%1
\item In your own words, what is a fibonacci sequence? 
%2
\item How do we solve problems involving fibonacci sequence? 

\end{enumerate}   
}

\def \TeachersGuideDayA {pp. 83--91}

\def \LMPagesDayA {pp. 50--54}

\def \TextbookPagesDayA {pp. 70--76}

\def \AdditionalMaterialsDayA {}

\def \OtherResourcesDayA {Flashcards}

\def \ReviewDayA {\input{/host-rootfs/storage/emulated/0/Documents/documents/latex/1920/Grade-10/1st/fibonacci-sequence/vs-fibonacci-sequence-input}}



\def \ExamplesDayA {}

\def \PracticeOneDayA {\input{/host-rootfs/storage/emulated/0/Documents/documents/latex/1920/Grade-10/1st/fibonacci-sequence/ps-fibonacci-sequence-input1}}

\def \PracticeTwoDayA {\input{/host-rootfs/storage/emulated/0/Documents/documents/latex/1920/Grade-10/1st/fibonacci-sequence/ps-fibonacci-sequence-input2}
}

\def \MasteryDayA {\input{/host-rootfs/storage/emulated/0/Documents/documents/latex/1920/Grade-10/1st/fibonacci-sequence/ps-fibonacci-sequence-input3}}



\def \EvaluationDayA {
\input{/host-rootfs/storage/emulated/0/Documents/documents/latex/1920/Grade-10/1st/fibonacci-sequence/qz-fibonacci-sequence-input} 
}

\def \RemediationDayA {}

\def \LessonDayB {Polynomial Function}

\def \LearningCompetenciesDayB {}

\def \ObjectivesDayB {
\item Describe a polynomial function; 
\item Determine the kind, the degree, the leading coefficient, and the constant term of a  polynomial function; and, 
\item Exhibit  patience and self-reliance  in solving problems.
}

\def \PurposeDayB {The purpose of this lesson is to enable the students to solve real life problems involving polynomial functions.}  

\def \ApplicationDayB { Let the students answer the following questions: 
\begin{enumerate}[label = \arabic*. ]
%1
\item In what real life situations or problems can we observe some examples of polynomial functions? 
%2
\item How can you apply your knowledge of polynomial functions in solving these real life problems? 

\end{enumerate}   
}

\def \GeneralizationDayB {Let the students answer the following questions: 
\begin{enumerate}[label = \arabic*. ]
%1
\item In your own words, what is a polynomial function? 
%2
\item How do we solve problems involving polynomial functions? 

\end{enumerate}   
}

\def \TeachersGuideDayB {pp. 62--66}

\def \LMPagesDayB {pp. 52--55}

\def \TextbookPagesDayB {pp. 62--66}

\def \AdditionalMaterialsDayB {}

\def \OtherResourcesDayB {Flashcards}

\def \ReviewDayB {\input{/host-rootfs/storage/emulated/0/Documents/documents/latex/1920/Grade-10/1st/polynomial-function/vs-polynomial-function-input}}



\def \ExamplesDayB {}

\def \PracticeOneDayB {\input{/host-rootfs/storage/emulated/0/Documents/documents/latex/1920/Grade-10/1st/polynomial-function/ps-polynomial-function-input1}}

\def \PracticeTwoDayB {\input{/host-rootfs/storage/emulated/0/Documents/documents/latex/1920/Grade-10/1st/polynomial-function/ps-polynomial-function-input2}
}

\def \MasteryDayB {\input{/host-rootfs/storage/emulated/0/Documents/documents/latex/1920/Grade-10/1st/polynomial-function/ps-polynomial-function-input3}}



\def \EvaluationDayB {
\input{/host-rootfs/storage/emulated/0/Documents/documents/latex/1920/Grade-10/1st/polynomial-function/qz-polynomial-function-input} 
}

\def \RemediationDayB {}

\def \LessonDayC {Synthetic Division}

\def \LearningCompetenciesDayC {}

\def \ObjectivesDayC {
\item Reiterate the steps in dividing polynomials using  synthetic division; 
\item Divide polynomials using synthetic division; and, 
\item Show independence and interest  in solving problems.
}

\def \PurposeDayC {The purpose of this lesson is to enable the students to solve real life problems involving synthetic division.}  

\def \ApplicationDayC { Let the students answer the following questions: 
\begin{enumerate}[label = \arabic*. ]
%1
\item In what real life situations or problems can we observe some examples of synthetic division? 
%2
\item How can you apply your knowledge of synthetic division in solving these real life problems? 

\end{enumerate}   
}

\def \GeneralizationDayC {Let the students answer the following questions: 
\begin{enumerate}[label = \arabic*. ]
%1
\item In your own words, what is  synthetic division? 
%2
\item How do we solve problems involving synthetic division? 

\end{enumerate}   
}

\def \TeachersGuideDayC {pp. 67--73}

\def \LMPagesDayC {pp. 56--61}

\def \TextbookPagesDayC {pp. 67--73}

\def \AdditionalMaterialsDayC {}

\def \OtherResourcesDayC {Flashcards}

\def \ReviewDayC {\input{/host-rootfs/storage/emulated/0/Documents/documents/latex/1920/Grade-10/1st/synthetic-division/vs-synthetic-division-input}}



\def \ExamplesDayC {}

\def \PracticeOneDayC {\input{/host-rootfs/storage/emulated/0/Documents/documents/latex/1920/Grade-10/1st/synthetic-division/ps-synthetic-division-input1}}

\def \PracticeTwoDayC {\input{/host-rootfs/storage/emulated/0/Documents/documents/latex/1920/Grade-10/1st/synthetic-division/ps-synthetic-division-input2}
}

\def \MasteryDayC {\input{/host-rootfs/storage/emulated/0/Documents/documents/latex/1920/Grade-10/1st/synthetic-division/ps-synthetic-division-input3}}



\def \EvaluationDayC {
\input{/host-rootfs/storage/emulated/0/Documents/documents/latex/1920/Grade-10/1st/synthetic-division/qz-synthetic-division-input} 
}

\def \RemediationDayC {}

\def \LessonDayD {Remainder Theorem}

\def \LearningCompetenciesDayD {}

\def \ObjectivesDayD {
\item Demonstrate  the remainder theorem; 
\item Compute the remainder of a polynomial using the remainder theorem; and, 
\item Exhibit determination and self-reliance in solving problems.
}

\def \PurposeDayD {The purpose of this lesson is to enable the students to solve real life problems involving the remainder theorem.}  

\def \ApplicationDayD { Let the students answer the following questions: 
\begin{enumerate}[label = \arabic*. ]
%1
\item In what real life situations or problems can we observe some examples of the remainder theorem? 
%2
\item How can you apply your knowledge of remainder theorem in solving these real life problems? 

\end{enumerate}   
}

\def \GeneralizationDayD {Let the students answer the following questions: 
\begin{enumerate}[label = \arabic*. ]
%1
\item In your own words, what is the remainder theorem? 
%2
\item How do we solve problems involving remainder theorem? 

\end{enumerate}   
}

\def \TeachersGuideDayD {pp. 74--78}

\def \LMPagesDayD {pp. 62--65}

\def \TextbookPagesDayD {pp. 74--78}

\def \AdditionalMaterialsDayD {}

\def \OtherResourcesDayD {Flashcards}

\def \ReviewDayD {\input{/host-rootfs/storage/emulated/0/Documents/documents/latex/1920/Grade-10/1st/remainder-theorem/vs-remainder-theorem-input}}



\def \ExamplesDayD {}

\def \PracticeOneDayD {\input{/host-rootfs/storage/emulated/0/Documents/documents/latex/1920/Grade-10/1st/remainder-theorem/ps-remainder-theorem-input1}}

\def \PracticeTwoDayD {\input{/host-rootfs/storage/emulated/0/Documents/documents/latex/1920/Grade-10/1st/remainder-theorem/ps-remainder-theorem-input2}
}

\def \MasteryDayD {\input{/host-rootfs/storage/emulated/0/Documents/documents/latex/1920/Grade-10/1st/remainder-theorem/ps-remainder-theorem-input3}}



\def \EvaluationDayD {
\input{/host-rootfs/storage/emulated/0/Documents/documents/latex/1920/Grade-10/1st/remainder-theorem/qz-remainder-theorem-input} 
}

\def \RemediationDayD {}

\def \LessonDayE {Factor Theorem}

\def \LearningCompetenciesDayE {}

\def \ObjectivesDayE {
\item %cogverbstart
Discuss  
%cogverbend
the factor theorem; 
\item %psyverbstart
Use
%psyverbend
the factor theorem to determine whether a binomial is a factor of a given polynomial; and, 
\item %affverbstart
Exhibit
%affverbend
%valsstart
perseverance and interest
%valsend
in solving problems.
}

\def \PurposeDayE {The purpose of this lesson is to enable the students to solve real life problems involving the factor theorem.}  

\def \ApplicationDayE { Let the students answer the following questions: 
\begin{enumerate}[label = \arabic*. ]
%1
\item In what real life situations or problems can we observe some examples of factor theorem? 
%2
\item How can you apply your knowledge of factor theorem in solving these real life problems? 

\end{enumerate}   
}

\def \GeneralizationDayE {Let the students answer the following questions: 
\begin{enumerate}[label = \arabic*. ]
%1
\item In your own words, what is the factor theorem? 
%2
\item How do we solve problems involving factor theorem? 

\end{enumerate}   
}

\def \TeachersGuideDayE {pp. 79--85}

\def \LMPagesDayE {pp. 66--71}

\def \TextbookPagesDayE {pp. 79--85}

\def \AdditionalMaterialsDayE {}

\def \OtherResourcesDayE {Flashcards}

\def \ReviewDayE {\input{/host-rootfs/storage/emulated/0/Documents/documents/latex/1920/Grade-10/1st/factor-theorem/vs-factor-theorem-input}}



\def \ExamplesDayE {}

\def \PracticeOneDayE {\input{/host-rootfs/storage/emulated/0/Documents/documents/latex/1920/Grade-10/1st/factor-theorem/ps-factor-theorem-input1}}

\def \PracticeTwoDayE {\input{/host-rootfs/storage/emulated/0/Documents/documents/latex/1920/Grade-10/1st/factor-theorem/ps-factor-theorem-input2}
}

\def \MasteryDayE {\input{/host-rootfs/storage/emulated/0/Documents/documents/latex/1920/Grade-10/1st/factor-theorem/ps-factor-theorem-input3}}



\def \EvaluationDayE {
\input{/host-rootfs/storage/emulated/0/Documents/documents/latex/1920/Grade-10/1st/factor-theorem/qz-factor-theorem-input} 
}

\def \RemediationDayE {}
