
\def \LessonDay {\makecell{Factoring the Greatest Common Monomial Factor}}

\def \LearningCompetenciesDay {}

\def \ObjectivesDay {
\item Compare the steps in factoring the greatest common monomial factor with distributive multiplication; 
\item Determine the factors of an algebraic expression using the greatest common monomial factor; and, 
\item Demonstrate enjoyment and perseverance in solving problems.
}

\def \PurposeDay {The purpose of this lesson is to enable the students to solve real life problems by factoring the greatest common monomial factor.}  

\def \ApplicationDay { Let the students answer the following questions: 
\begin{enumerate}[label = \arabic*. ]
%1
\item In what real life situations or problems can we observe some examples of factoring? 
%2
\item How can you apply your knowledge of factoring the greatest common monomial factor in solving these real life problems? 
\end{enumerate}   
}

\def \GeneralizationDay {Let the students answer the following questions: 
\begin{enumerate}[label = \arabic*. ]
%1
\item In your own words, how do we  factor the greatest common monomial factor? 
%2
\item How do we solve problems involving algebraic expressions that require  factoring the greatest common monomial factor? 
\end{enumerate}   
}

\def \TeachersGuideDay {pp. 30--35}

\def \LMPagesDay {pp. 26--30}

\def \TextbookPagesDay {pp. 33--39}

\def \AdditionalMaterialsDay {}

\def \OtherResourcesDay {Flashcards}

\def \ReviewDay {\input{/storage/emulated/0/Documents/documents/latex/1920/Grade-8/1st/factoring-the-greatest-common-monomial-factor/vs-factoring-the-greatest-common-monomial-factor-input}}


\def \ExamplesDay {}

\def \PracticeOneDay {\input{/storage/emulated/0/Documents/documents/latex/1920/Grade-8/1st/factoring-the-greatest-common-monomial-factor/ps-factoring-the-greatest-common-monomial-factor-input1}}

\def \PracticeTwoDay {\input{/storage/emulated/0/Documents/documents/latex/1920/Grade-8/1st/factoring-the-greatest-common-monomial-factor/ps-factoring-the-greatest-common-monomial-factor-input2}
}

\def \MasteryDay {\input{/storage/emulated/0/Documents/documents/latex/1920/Grade-8/1st/factoring-the-greatest-common-monomial-factor/ps-factoring-the-greatest-common-monomial-factor-input3}}

\def \EvaluationDay {
\input{/storage/emulated/0/Documents/documents/latex/1920/Grade-8/1st/factoring-the-greatest-common-monomial-factor/qz-factoring-the-greatest-common-monomial-factor-input} 
}

\def \RemediationDay {}
