
\def \LessonDay {\makecell{Arithmetic Sequences}}

\def \LearningCompetenciesDay {}

\def \ObjectivesDay {
\item Execute the steps in finding the rule of a given arithmetic sequence; 
\item Find the next terms of a given arithmetic sequence; and, 
\item Project interest and enjoyment in solving problems.
}

\def \TeachersGuideDay {pp. 11--21}

\def \LMPagesDay {pp. 7--13}

\def \TextbookPagesDay {pp. 9--18}

\def \AdditionalMaterialsDay {}

\def \OtherResourcesDay {Flashcards}

\def \ReviewDay {\input{/storage/emulated/0/Documents/documents/latex/1920/Grade-10/1st/arithmetic-sequences/vs-arithmetic-sequences-input}}

\def \PurposeDay {The purpose of this lesson is to enable the students to solve real life problems involving arithmetic sequences.}  

\def \ExamplesDay {Some examples of arithmetic sequences are the following: 
\begin{enumerate}[label = \arabic*. ]
%1
\item \hspce $14, 6, -2,... a_{28}$
%2
\item \hspce  $3, 5, 7,... a_{21}$
\item \hspce $1.4, 4.5, 7.6,... a_{51}$
\end{enumerate}   
}

\def \PracticeOneDay {\input{/storage/emulated/0/Documents/documents/latex/1920/Grade-10/1st/arithmetic-sequences/ps-arithmetic-sequences-input1}}

\def \PracticeTwoDay {\input{/storage/emulated/0/Documents/documents/latex/1920/Grade-10/1st/arithmetic-sequences/ps-arithmetic-sequences-input2}
}

\def \MasteryDay {\input{/storage/emulated/0/Documents/documents/latex/1920/Grade-10/1st/arithmetic-sequences/ps-arithmetic-sequences-input3}}

\def \ApplicationDay { Let the students answer the following questions: 
\begin{enumerate}[label = \arabic*. ]
%1
\item In what real life situations or problems can we observe some examples of arithmetic sequences? 
%2
\item How can you apply your knowledge of arithmetic sequences in solving these real life problems? 
%3
%\item 
\end{enumerate}   
}

\def \GeneralizationDay {Let the students answer the following questions: 
\begin{enumerate}[label = \arabic*. ]
%1
\item In your own words, what are arithmetic sequences? 
%2
\item How do we solve problems involving arithmetic sequences? 
%3
%\item 
\end{enumerate}   
}

\def \EvaluationDay {
\input{/storage/emulated/0/Documents/documents/latex/1920/Grade-10/1st/arithmetic-sequences/qz-arithmetic-sequences-input} 
}

\def \RemediationDay {}
