
\def \LessonDay {Graphical Solutions of Systems of Linear Inequalities}

\def \LearningCompetenciesDay {}

\def \ObjectivesDay {
\item %cogverbstart
Solve
%cogverbend
rational equations; 
\item %psyverbstart
Find
%psyverbend
solutions to rational equations; and, 
\item %affverbstart
Demonstrate
%affverbend
%valsstart
determination and self-reliance
%valsend
in solving problems.
}

\def \PurposeDay {The purpose of this lesson is to enable the students to solve real life problems involving rational equations.}  

\def \ApplicationDay { Let the students answer the following questions: 
\begin{enumerate}[label = \arabic*. ]
%1
\item In what real life situations or problems can we observe some examples of rational equations? 
%2
\item How can you apply your knowledge of rational equations in solving these real life problems? 
\end{enumerate}   
}

\def \GeneralizationDay {Let the students answer the following questions: 
\begin{enumerate}[label = \arabic*. ]
%1
\item In your own words, what are rational equations? 
%2
\item How do we solve rational equations? 
\end{enumerate}   
}

\def \TeachersGuideDay {pp. 245--252}

\def \LMPagesDay {pp. 239--245}

\def \TextbookPagesDay {pp. 243--249}

\def \AdditionalMaterialsDay {}

\def \OtherResourcesDay {Flashcards}

\def \ReviewDay {\input{/storage/emulated/0/Documents/documents/latex/1920/Grade-8/2nd/graphical-solutions-of-systems-of-linear-inequalities/vs-graphical-solutions-of-systems-of-linear-inequalities-input}}


\def \ExamplesDay {}

\def \PracticeOneDay {\input{/storage/emulated/0/Documents/documents/latex/1920/Grade-8/2nd/graphical-solutions-of-systems-of-linear-inequalities/ps-graphical-solutions-of-systems-of-linear-inequalities-input1}}

\def \PracticeTwoDay {\input{/storage/emulated/0/Documents/documents/latex/1920/Grade-8/2nd/graphical-solutions-of-systems-of-linear-inequalities/ps-graphical-solutions-of-systems-of-linear-inequalities-input2}
}

\def \MasteryDay {\input{/storage/emulated/0/Documents/documents/latex/1920/Grade-8/2nd/graphical-solutions-of-systems-of-linear-inequalities/ps-graphical-solutions-of-systems-of-linear-inequalities-input3}}

\def \EvaluationDay {
\input{/storage/emulated/0/Documents/documents/latex/1920/Grade-8/2nd/graphical-solutions-of-systems-of-linear-inequalities/qz-graphical-solutions-of-systems-of-linear-inequalities-input} 
}

\def \RemediationDay {}
