
\def \LessonDay {Finding Integral Zeros}

\def \LearningCompetenciesDay {}

\def \ObjectivesDay {
\item %cogverbstart
Relate
%cogverbend
the finding integral zeros; 
\item %psyverbstart
Find
%psyverbend
the finding integral zeros to determine whether a binomial is a factor of a given polynomial; and, 
\item %affverbstart
Show
%affverbend
%valsstart
enjoyment and interest
%valsend
in solving problems.
}

\def \PurposeDay {The purpose of this lesson is to enable the students to solve real life problems involving the finding integral zeros.}  

\def \ApplicationDay { Let the students answer the following questions: 
\begin{enumerate}[label = \arabic*. ]
%1
\item In what real life situations or problems can we observe some examples of finding integral zeros? 
%2
\item How can you apply your knowledge of finding integral zeros in solving these real life problems? 

\end{enumerate}   
}

\def \GeneralizationDay {Let the students answer the following questions: 
\begin{enumerate}[label = \arabic*. ]
%1
\item In your own words, what is the finding integral zeros? 
%2
\item How do we solve problems involving finding integral zeros? 

\end{enumerate}   
}

\def \TeachersGuideDay {pp. 91--97}

\def \LMPagesDay {pp. 76--81}

\def \TextbookPagesDay {pp. 91--97}

\def \AdditionalMaterialsDay {}

\def \OtherResourcesDay {Flashcards}

\def \ReviewDay {\input{/storage/emulated/0/Documents/documents/latex/1920/Grade-10/1st/finding-integral-zeros/vs-finding-integral-zeros-input}}



\def \ExamplesDay {}

\def \PracticeOneDay {\input{/storage/emulated/0/Documents/documents/latex/1920/Grade-10/1st/finding-integral-zeros/ps-finding-integral-zeros-input1}}

\def \PracticeTwoDay {\input{/storage/emulated/0/Documents/documents/latex/1920/Grade-10/1st/finding-integral-zeros/ps-finding-integral-zeros-input2}
}

\def \MasteryDay {\input{/storage/emulated/0/Documents/documents/latex/1920/Grade-10/1st/finding-integral-zeros/ps-finding-integral-zeros-input3}}



\def \EvaluationDay {
\input{/storage/emulated/0/Documents/documents/latex/1920/Grade-10/1st/finding-integral-zeros/qz-finding-integral-zeros-input} 
}

\def \RemediationDay {}
