% cd /storage/emulated/0/Documents/documents/latex/1920/Grade-10/tests/math-month/ && pdflatex easy-round-logic.tex && termux-open easy-round-logic.pdf

\documentclass[11pt]{article}
\usepackage[letterpaper, landscape, margin=0.5in]{geometry}

\input{/storage/emulated/0/Documents/documents/latex/1920/common-preamble-2019} 

\pagenumbering{gobble}

\begin{document} 

\textbf{Riddles and Verbal Puzzles}
\begin{enumerate}[label = \arabic*. ]
%\begin{multicols}{2}

%1
\item What is greater than God,
more evil than the devil? The poor have it, the rich need it,
and if you eat it, you'll die. \hfill Answer: Nothing 

%2
\item What has hands but can not clap? \hfill Answer: Clock  

%3
\item What is made of water but if you put it into water it will die? \hfill Answer: Ice

%4
\item Im tall when I'm young and I'm short when I'm old. What am I? \hfill Answer: Candle

%5
\item Who makes it, has no need of it. Who buys it, has no use for it. Who uses it can neither see nor feel it. What is it? \hfill Answer: Coffin 

%6
\item You can drop me from the tallest building and I'll be fine, but if you drop me in water I die. What am I? \hfill Answer: Paper

%7
\item What has an eye but can not see? \hfill Answer: Needle

%8
\item What gets wetter and wetter the more it dries? \hfill Answer: Towel 

%9
\item David's height is six feet. He's an assistant at a butcher's shop and wears size 9 shoes. What does he weigh? \hfill Answer: Meat

%10
\item Take off my skin, I won't cry, but you will! What am I? \hfill Answer: Onion 

%11
\item Feed me and I live, yet give me a drink and I die. What am I? \hfill Answer: Fire

%12
\item Which word in the dictionary is spelled incorrectly? \hfill Answer: Incorrectly 

%13
\item What occurs once in every minute, twice in every moment, yet never in a thousand years? \hfill Answer: Letter M

%14
\item What five-letter word becomes shorter when you add two letters to it? \hfill Answer: Short

%15
\item Cathy has twelve black socks and twelve white socks in her drawer. In complete darkness, and without looking, how many socks must she take from the drawer in order to be sure to get a pair that match?  \hfill Answer: 3

%16
\item Mary's mum has four children. The first child is called April. The second is called may. The third is called June. What is the name of fourth child? \hfill Answer: Mary

%17
\item Some months have 30 days; others have 31. How many months have 28 days? \hfill Answer: 12

%18
\item If you had only one match and entered a cold and dark room where there was an oil heater, an oil lamp and a candle, which would you light first? \hfill Answer: The match

%19
\item If you divide 30 by half and add 10, what number do you get? \hfill Answer: 70

%20
\item A man builds a house with all 4 sides facing south. A bear walks past the house. What color is the bear? \hfill Answer: White

%21
\item There are three houses -- a white one, a red one, and a blue one. The red one is on the left and the blue one is on the right. Where is the white house? \hfill Answer: In Washington D.C.

%22
\item How many of each species of animals did Moses take on the ark with him? \hfill Answer: None

%23
\item What is the next letter in the following sequence: J, F, M, A, M, J, \blank? \hfill Answer: J

%24
\item I am an odd number. Take away one letter and I become even. What number am I? \hfill Answer: Seven 

%25
\item What three numbers have the same sum and the same product? \hfill Answer: 1, 2, and 3

%26
\item I'm full of holes, yet I'm full of water. What am I? \hfill Answer: Sponge 

%27
\item How many times can you subtract the number 2 from the number 32? \hfill Answer: Once

%28
\item If you were running a race, and you passed the person in second place, what place would you be in now? \hfill Answer: Second place 

%29
\item During which month do people sleep the least?  \hfill Answer: February 

%30
\item He has married many women, but has never been married. Who is he? \hfill Answer: Priest 

%31
\item What is at the end of a rainbow? \hfill Answer: The letter W. 

%32
\item What is as light as a feather, but even the world's strongest man cannot hold it for more than a minute?  \hfill Answer: Breath 

%33
\item \hfill Answer: 

%34
\item \hfill Answer: 

%35
\item \hfill Answer: 

%36
\item \hfill Answer: 

%37
\item \hfill Answer: 

%38
\item \hfill Answer: 

%39
\item \hfill Answer: 

%40
\item \hfill Answer: 

%\end{multicols} 
\end{enumerate}  

\textbf{Visual and Mathematical  Puzzles}
%\begin{center}
%\vspace*{2ex}
%\scalebox{1}{
%oindent\begin{minipage}{\textwidth}
{\begin{enumerate}[label = \arabic*. ]
%\begin{multicols}{2}
%1
\item Using only addition, how do you add eight 8's and get the number 1000? \hfill Answer: $888 + 88 + 8 + 8 + 8 = 1000$
%2
\item \hfill Answer: 
%3
\item \hfill Answer: 
%4
\item \hfill Answer: 
%5
\item \hfill Answer: 
%6
\item \hfill Answer: 
%7
\item \hfill Answer: 
%8
\item \hfill Answer: 
%9
\item \hfill Answer: 
%10
\item \hfill Answer: 
%\end{multicols} 
\end{enumerate}}
%\end{minipage}}
%\end{center}  





     
\end{document} 