% cd /storage/emulated/0/Documents/documents/latex/1920/Grade-10/tests/math-month/ && pdflatex mathtinee-mechanics.tex && termux-open mathtinee-mechanics.pdf

\documentclass[11pt]{article}
\usepackage[letterpaper, portrait, margin=0.5in]{geometry}

\input{/storage/emulated/0/Documents/documents/latex/1920/common-preamble-2019} 

\pagenumbering{gobble}

\begin{document} 

\begin{center}
\textbf{Search for the Math-tinee Idol 2019}
\end{center} 

\textbf{General Contest Mechanics} 
\begin{enumerate}[label = \arabic*. ]
%\begin{multicols}{2}
%1
\item Each contestant must be a bona fide student of Sauyo High School. 
%2
\item Twelve finalists who were chosen from the Elimination round will be rated based on their talent, introduction and pickup line, casual wear, sports wear, and formal wear. The talent portion was already completed so the final round will be focused on the introduction and the three wear competitions. 
%3
\item The Introduction will be rated based on the following criteria: 
\begin{enumerate}[label = \alph*. ]
%\begin{multicols}{2}
%1
\item Confidence \& Poise (30 Points)
%2
\item Uniqueness \& Style (25 Points)
%3
\item Pickup Line (20 Points)
%4
\item Stage Presence (15 Points)
%5 
\item Overall Impression (10 Points)
%\end{multicols} 
\end{enumerate}  
The highest possible score is 100 points. 
%4
\item The casual wear, sports wear, and formal wear competitions will be rated based on the following criteria: 
\begin{enumerate}[label = \alph*. ]
%\begin{multicols}{2}
%1
\item Poise \& Projection (30\%)
%2
\item Aesthetics (25\%)
%3
\item Suitability of Attire (20\%)
%4
\item Stage Presence (15\%)
%5 
\item Audience Impact (10\%)
%\end{multicols} 
\end{enumerate}  
The highest possible score is 100\%. 
%5 
\item The finalists will be ranked based on their scores in the introduction and the three wear competitions. The top 5 finalists, whom we will call the ``Idol 5'', will compete in the Question and Answer Portion. In the Question and Answer Portion, the scores accumulated from the introduction and the wear competitions will be set back to zero. 
\item The Question and Answer Portion will be rated based on the following criteria: 
\begin{enumerate}[label = \alph*. ]
%\begin{multicols}{2}
%1
\item Creativity of Answer (40 Points)
%2
\item Confidence (30 Points)
%3
\item Clarity of Thoughts (30 Points)

%\end{multicols} 
\end{enumerate}  
The highest possible score is 100 points. 
\item The ``Idol 5'' will be ranked based on their scores in the Question and Answer Portion. The top 3 finalists will be given the titles of Second Runner Up, First Runner Up, and the Math-tinee Idol 2019.
%\end{multicols} 
\end{enumerate}  


\end{document} 