
\def \LessonDay {\makecell{Cube of a Binomial}}

\def \LearningCompetenciesDay {}

\def \ObjectivesDay {
\item Discuss the steps in finding the cube of a binomial; 
\item Solve the cube of a binomial; and, 
\item Demonstrate interest and willingness in solving problems.
}

\def \PurposeDay {The purpose of this lesson is to enable the students to solve real life problems involving the cube of a binomial.}  

\def \ApplicationDay { Let the students answer the following questions: 
\begin{enumerate}[label = \arabic*. ]
%1
\item In what real life situations or problems can we observe some examples of cubing binomials? 
%2
\item How can you apply your knowledge of cubing binomials in solving these real life problems? 
\end{enumerate}   
}

\def \GeneralizationDay {Let the students answer the following questions: 
\begin{enumerate}[label = \arabic*. ]
%1
\item In your own words, how do we get  the cube of a binomial? 
%2
\item How do we solve problems involving the cube of a binomial? 
\end{enumerate}   
}

\def \TeachersGuideDay {pp. 22--29}

\def \LMPagesDay {pp. 19--25}

\def \TextbookPagesDay {pp. 24--32}

\def \AdditionalMaterialsDay {}

\def \OtherResourcesDay {Flashcards}

\def \ReviewDay {\input{/storage/emulated/0/Documents/documents/latex/1920/Grade-8/1st/cube-of-a-binomial/vs-cube-of-a-binomial-input}}


\def \ExamplesDay {}

\def \PracticeOneDay {\input{/storage/emulated/0/Documents/documents/latex/1920/Grade-8/1st/cube-of-a-binomial/ps-cube-of-a-binomial-input1}}

\def \PracticeTwoDay {\input{/storage/emulated/0/Documents/documents/latex/1920/Grade-8/1st/cube-of-a-binomial/ps-cube-of-a-binomial-input2}
}

\def \MasteryDay {\input{/storage/emulated/0/Documents/documents/latex/1920/Grade-8/1st/cube-of-a-binomial/ps-cube-of-a-binomial-input3}}

\def \EvaluationDay {
\input{/storage/emulated/0/Documents/documents/latex/1920/Grade-8/1st/cube-of-a-binomial/qz-cube-of-a-binomial-input} 
}

\def \RemediationDay {}
