
\def \LessonDay {Radii and Chords}

\def \LearningCompetenciesDay {}

\def \ObjectivesDay {
\item %cogverbstart
Recall
%cogverbend
the radii and chords; 
\item %psyverbstart
Compute
%psyverbend
the radii and chords to determine whether a binomial is a factor of a given polynomial; and, 
\item %affverbstart
Demonstrate
%affverbend
%valsstart
enjoyment and willingness
%valsend
in solving problems.
}

\def \PurposeDay {The purpose of this lesson is to enable the students to solve real life problems involving the radii and chords.}  

\def \ApplicationDay { Let the students answer the following questions: 
\begin{enumerate}[label = \arabic*. ]
%1
\item In what real life situations or problems can we observe some examples of radii and chords? 
%2
\item How can you apply your knowledge of radii and chords in solving these real life problems? 

\end{enumerate}   
}

\def \GeneralizationDay {Let the students answer the following questions: 
\begin{enumerate}[label = \arabic*. ]
%1
\item In your own words, what is the radii and chords? 
%2
\item How do we solve problems involving radii and chords? 

\end{enumerate}   
}

\def \TeachersGuideDay {pp. 131--134}

\def \LMPagesDay {pp. 120--123}

\def \TextbookPagesDay {pp. 128--132}

\def \AdditionalMaterialsDay {}

\def \OtherResourcesDay {Flashcards}

\def \ReviewDay {\input{/storage/emulated/0/Documents/documents/latex/1920/Grade-10/2nd/radii-and-chords/vs-radii-and-chords-input}}



\def \ExamplesDay {}

\def \PracticeOneDay {\input{/storage/emulated/0/Documents/documents/latex/1920/Grade-10/2nd/radii-and-chords/ps-radii-and-chords-input1}}

\def \PracticeTwoDay {\input{/storage/emulated/0/Documents/documents/latex/1920/Grade-10/2nd/radii-and-chords/ps-radii-and-chords-input2}
}

\def \MasteryDay {\input{/storage/emulated/0/Documents/documents/latex/1920/Grade-10/2nd/radii-and-chords/ps-radii-and-chords-input3}}



\def \EvaluationDay {
\input{/storage/emulated/0/Documents/documents/latex/1920/Grade-10/2nd/radii-and-chords/qz-radii-and-chords-input} 
}

\def \RemediationDay {}
